---
title: "Field emissions"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
---

```{r load_libraries, include=FALSE}
  library(tidyverse)
  library(knitr)
```

```{r global_options, include=FALSE}
  knitr::opts_chunk$set(fig.path ='figures/', warning = FALSE, message = FALSE, cache = FALSE)
```

# Load files

* functions 

```{r functions}
  source("../r_scripts/functions.R")
  source("../r_scripts/plots.R")
```

* pollutant data

```{r load_data}
  temp <- readRDS("../r_files/field_temp_merged.RDS")
  grav <- readRDS("../r_files/field_grav_merged.RDS")
  aqe <- readRDS("../r_files/field_aqe_merged.RDS")
  aqe_bkgd <- readRDS("../r_files/field_aqe_bkgd.RDS")
  temp <- readRDS("../r_files/field_temp_merged.RDS")
  bc <- readRDS("../r_files/field_ma_merged.RDS")
  bc_bkgd <- readRDS("../r_files/field_ma_bkgd.RDS")
```

* constants

```{r load_constants}
  fuel_properties <- readRDS("../r_files/fuel_properties.RDS")
  pol_properties <- readRDS("../r_files/pol_properties.RDS")
```

* metadata

```{r load_metadata}
  times <- readRDS("../r_files/field_test_times.RDS")
  samples <- readRDS("../r_files/field_samples.RDS")
  fuel_wgts <- readRDS("../r_files/field_fuel_wgts.RDS")
```

# Gas analyzer

* calculate test average

```{r aqe_test_avg}
  aqe <- aqe %>%
         dplyr::filter(qc != "bad") %>%
         dplyr::group_by(hh_id, var) %>%
         dplyr::summarise(mix_ratio = mean(val, na.rm = TRUE),
                          units = first(units),
                          qc = first(qc)) %>%
        dplyr::ungroup()
```

* subtract background 

```{r sub_bkgd}
  aqe <- aqe %>%
         dplyr::left_join(dplyr::select(aqe_bkgd$mean, hh_id, var, val), by = c("var", "hh_id")) %>%
         dplyr::rename(bkgd_mix_ratio = val) %>%
         dplyr::mutate(mix_ratio = mix_ratio - bkgd_mix_ratio) %>%
         dplyr::select(-bkgd_mix_ratio)
```

* calculate mce

```{r}
  mce <- aqe %>%
         tidyr::spread(var, mix_ratio) %>%
         dplyr::mutate(mce = co2 / (co + co2)) %>%
         dplyr::mutate(units = "") %>%
         dplyr::mutate(pol = "co:co2") %>%
         dplyr::select(hh_id, pol, units, qc, mce) %>%
         tidyr::gather("var", "val", 5)
```



* update test qc based on background qc

```{r update_qc}
  # add code for this
```

* convert mixing ratios to mass conc (assuming constant T and P)

```{r calc_mass_conc}
  aqe <- aqe %>%
         dplyr::left_join(pol_properties, by = c("var" = "pol")) %>%
         dplyr::mutate(mass_conc = convert_ppmv_mgm3(ppmv = mix_ratio, mw = mw)) %>%
         dplyr::select(-units)
```

* calculate the mass concentration of carbon

```{r calc_carbon}
  aqe <- aqe %>%
         dplyr::mutate(carbon_mass_conc = mass_conc * (mw_c() * num_c / mw))
```

* tidy aqe data

```{r tidy_aqe}
  aqe <- aqe %>%
         dplyr::select(hh_id, var, qc, mass_conc, carbon_mass_conc) %>%
         dplyr::rename(pol = var) %>%
         tidyr::gather("var", "val", 4:5) %>%
         dplyr::mutate(units = "mg_m3",
                       units = if_else(var == "carbon_mass_conc", "ug_m3 of carbon", units))
```

# Gravimetric data

* calculate concentrations and tidy grav

```{r calc_tidy}
  grav <- grav %>%
          dplyr::filter(qc != "bad") %>%
          dplyr::mutate(mass_conc = (mass * 1000) / (avg_flow * dur),
                        carbon_mass_conc = NA) %>%
          dplyr::select(hh_id, pol, qc, mass_conc, carbon_mass_conc) %>%
          tidyr::gather("var", "val", 4:5) %>%
          dplyr::mutate(units = "ug_m3",
          units = if_else(var == "carbon_mass_conc", "ug_m3 of carbon", units))
```

# Flue temp

* calculate average and tidy flue temp

```{r temp_test_avg}
  temp <- temp %>%
          dplyr::filter(qc != "bad") %>%
          dplyr::group_by(hh_id) %>%
          dplyr::summarise(avg_temp = mean(val, na.rm = TRUE),
                           prct95 = quantile(val, .95, na.rm = TRUE),
                           units = first(units),
                           var = first(var),
                           qc = first(qc)) %>%
          dplyr::ungroup() %>%
          dplyr::rename(pol = var) %>%
          dplyr::group_by(hh_id) %>%
          dplyr::mutate(prct95 = avg_temp/prct95) %>%
          dplyr::select(hh_id, pol, qc, avg_temp, prct95, units) %>%
          tidyr::gather("var", "val", 4:5)
```

# Black carbon

* calculate test average

```{r bc_test_avg}
  bc <- bc %>%
        dplyr::filter(qc != "bad") %>%
        dplyr::group_by(hh_id) %>%
        dplyr::summarise(mass_conc = mean(val, na.rm = TRUE),
                         units = first(units),
                         qc = first(qc)) %>%
        dplyr::ungroup()
```

* subtract background 

```{r bc_sub_bkgd}
  bc <- bc %>%
        dplyr::left_join(dplyr::select(bc_bkgd$mean, hh_id, val), by = c("hh_id")) %>%
        dplyr::rename(bkgd_bc_conc = val) %>%
        dplyr::mutate(mass_conc = mass_conc - bkgd_bc_conc) %>%
        dplyr::select(-bkgd_bc_conc)
```

* tidy bc data

```{r tidy_abc}
  bc <- bc %>%
        dplyr::mutate(pol = "bc") %>%
        tidyr::gather("var", "val", 2) %>%
        dplyr::mutate(units = "ug_m3")
```

# Combine all instrument data

```{r combine_save}
  emissions <- dplyr::bind_rows(aqe, grav, temp, bc, mce)
```

# Plot all data for qc

* add bad tests and remove

```{r emissions_qc}
  emissions$qc[emissions$hh_id == "IN19" &  emissions$var == "avg_temp"] <- "bad"
  emissions$qc[emissions$hh_id == "IN19" &  emissions$var == "prct95"] <- "bad"
```

* plot qc

```{r qc_plots, fig.height=12, fig.width=12, echo=FALSE}
  ggplot(emissions, aes(x = hh_id, y = val, colour = qc)) + 
    geom_point() + 
    theme_bw() +
    theme(legend.position = "top",
          text = element_text(size = 20),
          axis.text.x = element_text(angle = 45, hjust = 1, size = 12)) +
    facet_wrap(pol~var, scales = "free")
```

* remove bad tests

```{r remove_bad}
  emissions <- dplyr::filter(emissions, qc != "bad")
```

# Calculate emissions factors

```{r extract_test_meta, include=FALSE}
  #metadata <- samples %>%
   #           dplyr::select(-date)
```

```{r add_test_time, include=FALSE}
  dur <- times %>%
         dplyr::filter(var == "dur") %>%
         tidyr::spread(var, value) %>%
         dplyr::select(hh_id, dur) 
```

```{r add_fuel_info, include=FALSE}
  fuel_avg <- fuel_properties %>%
              dplyr::group_by(fuel, var) %>%
              dplyr::filter(qc != "bad") %>%
              dplyr::summarise(val = mean(val), qc = first(qc)) %>%
              tidyr::spread(var, val) %>%
              dplyr::left_join(dplyr::select(samples, hh_id, fuel_type),
                               by = c("fuel" = "fuel_type")) %>%
              dplyr::filter(!is.na(hh_id))

#  fuel <- fuel_properties %>%
#          dplyr::group_by(hh_id, fuel, var) %>%
#          dplyr::summarise(val = mean(val),
#                           qc = first(qc)) %>%
#          tidyr::spread(var, val) %>%
#          dplyr::right_join(dplyr::select(samples, fuel_type, hh_id),
#                            by = c("fuel" = "fuel_type", "hh_id")) %>%
#          dplyr::coalesce(fuel_avg)
```

```{r combine_meta, include=FALSE}
 # metadata <- metadata %>%
  #            dplyr::left_join(dur, by = "hh_id") %>%
   #           tidyr::gather("var", "val", 3:5) %>%
    #          dplyr::bind_rows(fuel)
```

```{r cal_fuel}

  # need to figure out how to carry through units and qc

  meta <- emissions %>%
             dplyr::filter(grepl("co2|co", pol) & var == "carbon_mass_conc") %>%
             dplyr::group_by(hh_id) %>%
             dplyr::summarise(total_carbon_conc = sum(val)) %>%
             dplyr::left_join(dplyr::select(fuel_avg, hh_id, carbon, lhv), by = "hh_id") %>%
             dplyr::mutate(carbon = carbon / 100) %>%
             dplyr::left_join(dur, by = "hh_id") %>%
             dplyr::left_join(dplyr::select(fuel_wgts, hh_id, fuel_wgt))
```

```{r calc_pm}
  pm25_ef <- emissions %>%
             dplyr::filter(pol == "pm2.5" & var == "mass_conc") %>%
             tidyr::spread(var, val) %>%
             dplyr::left_join(meta, by = "hh_id") %>%
             dplyr::group_by(hh_id) %>%
             dplyr::mutate(pm_ef = (mass_conc * carbon) / total_carbon_conc) %>%
             dplyr::mutate(pm_mass = pm_ef * fuel_wgt) %>%
             dplyr::mutate(pm_rate = pm_ef * (fuel_wgt / dur) * 1000) %>%
             dplyr::mutate(pm_ef_energy = (pm_ef * 1000) / (lhv / 1000)) %>%
             dplyr::mutate(firepower = (lhv * fuel_wgt) / (dur * 60)) %>%
             dplyr::select(hh_id, pol, qc, pm_ef, pm_ef_energy, pm_rate, pm_mass, firepower) %>%
             tidyr::gather("var", "val", 4:8) %>%
             dplyr::mutate(units = NA)
```

```{r calc_bc}
    bc_ef <- emissions %>%
             dplyr::filter(pol == "bc" & var == "mass_conc") %>%
             tidyr::spread(var, val) %>%
             dplyr::left_join(meta, by = "hh_id") %>%
             dplyr::group_by(hh_id) %>%
             dplyr::mutate(bc_ef = (mass_conc * carbon) / total_carbon_conc) %>%
             dplyr::mutate(bc_mass = bc_ef * fuel_wgt) %>%
             dplyr::mutate(bc_rate = bc_ef * (fuel_wgt / dur) * 1000) %>%
             dplyr::mutate(bc_ef_energy = (bc_ef * 1000) / (lhv / 1000)) %>%
             dplyr::select(hh_id, pol, qc, bc_ef, bc_ef_energy, bc_rate, bc_mass) %>%
             tidyr::gather("var", "val", 4:7) %>%
             dplyr::mutate(units = NA)
```

```{r bind_efs}
  emissions <- dplyr::bind_rows(emissions, pm25_ef, bc_ef)
```

# Plot PM EF vs. avg temp

```{r}
  firepower <- emissions %>%
               dplyr::filter(var == "firepower" | var == "avg_temp" | var == "prct95") %>%
               dplyr::select(-pol, -units, -qc) %>%
               tidyr::spread(var, val)

  p_emissions <- emissions %>%
                 dplyr::filter(var != "carbon_mass_conc", var != "firepower", var != "avg_temp", var != "prct95") %>%
                 dplyr::filter(grepl("pm2.5|bc", pol)) %>%
                 dplyr::left_join(firepower, by = "hh_id") %>%
                 dplyr::left_join(dplyr::select(samples, hh_id, stove_type), by = "hh_id")
```

## Firepower 

```{r, fig.height=20, fig.width=12}
  field_plot_dot_line(p_emissions, y_var = "val", y_label = "variable")
```

## Avg flue temp

```{r, echo=FALSE, fig.height=20, fig.width=12}
  field_plot_dot_line(p_emissions, y_var = "val", y_label = "variable",
                      x_var = "avg_temp", x_label = "average temperature")
```

## Avg flue temp normalized by 95th percentile

```{r, echo=FALSE, fig.height=20, fig.width=12}
  field_plot_dot_line(p_emissions, y_var = "val", y_label = "variable",
                      x_var = "prct95", x_label = "average temperature/95th prctile")
```

# Save file

```{r}
  saveRDS(emissions, "../r_files/field_emissions.RDS")
```

