---
title: "temp"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
---

```{r global_options, include=FALSE}
  knitr::opts_chunk$set(fig.path='figures/', warning=FALSE, message=FALSE, cache=TRUE)
```

```{r library}
  library(tidyverse)
```

```{r functions}
  source("../r_scripts/functions.r")
  source("../r_scripts/plots.r")
```

# Load data

* flue temperature

```{r load_data}
  temp <- readRDS("../r_files/field_temp.rds")
```

* metadata

```{r load_meta}
  test_times <- readRDS("../r_files/field_test_times.rds")
  samples <- readRDS("../r_files/field_samples.rds")
  temp_meta <- readRDS("../r_files/field_temp_meta.rds")
  notes <- readRDS("../r_files/field_notes.rds")
```

# Tidy

* add household id information

```{r add_hh_id}
  temp_merged_all <- dplyr::left_join(temp, dplyr::select(temp_meta, logger_id, hh_id, field_site),
                                            by = "logger_id") %>%
                     dplyr::filter(!is.na(hh_id)) %>%
                     dplyr::mutate(hh_id = as.factor(hh_id)) %>%  # should alaready be factor
                     dplyr::select(-logger_id)
```

* fix India times

```{r fix_times}
  temp_merged_all <- dplyr::mutate(temp_merged_all,
                                   datetime = ifelse(field_site == "india",
                                                     format(datetime, tz = "Asia/Calcutta"), datetime)) %>%
                     dplyr::mutate(datetime = as.POSIXct(datetime, tz = "Asia/Calcutta")) %>%
                     dplyr::mutate(date = as.Date(datetime)) %>%
                     dplyr::mutate(time = as.numeric(substr(datetime, 12, 13)) * 60 * 60 + 
                                     as.numeric(substr(datetime, 15, 16)) * 60 +
                                     as.numeric(substr(datetime, 18, 19)))
```

* add units
```{r add_units}
  temp_merged_all <- dplyr::mutate(temp_merged_all, units = "degrees Celsius")
```

# QC

## flags from notes

* extract notes

```{r get_notes}
  notes <- dplyr::filter(notes, grepl("temp|all", inst) == TRUE)
```

* apply flags: `bad` preceeds `maybe` preceeds `good`

```{r flags}
  flags <- dplyr::select(notes, hh_id, qc) %>%
           dplyr::group_by(hh_id) %>%
           dplyr::arrange(qc) %>%
           dplyr::summarise(qc = first(qc))
```

* merge flags with data

```{r merge_flags}
  # fix warning
  temp_merged_all <- dplyr::left_join(temp_merged_all, flags, by = "hh_id") %>%
                     dplyr::mutate(qc = as.factor(ifelse(is.na(qc), "ok", as.character(qc)))) %>%
                     dplyr::mutate(qc = forcats::lvls_expand(qc, c("bad", "maybe", "ok")))
```

## additional bad tests

```{r bad_tests_1}
  temp_merged_all$qc[temp_merged_all$hh_id == "IN10"] <- "bad"
```

## Filter only test

```{r get_times}
  times <- dplyr::filter(test_times, var == "sample_start" | var == "sample_end") %>%
           tidyr::spread(var, value) %>%
           dplyr::rename(start = sample_start, end = sample_end)
```

```{r filter_tests}
  temp_merged <- filter_times(times, temp_merged_all)
```

## additional bad tests

```{r bad_tests_2}

  temp_merged$qc[temp_merged$hh_id == "IN12"] <- "maybe"
  temp_merged$qc[temp_merged$hh_id == "IN17"] <- "maybe"
  temp_merged$qc[temp_merged$hh_id == "IN18"] <- "maybe"

```

# Plots

## all data

```{r plot_all_temp_data, fig.width=12, fig.height=10}
  field_timeseries_plot(temp_merged_all, "temp")
```

## test data only

```{r plot_test_temp, fig.width=12, fig.height=10}
  # duplicates coming in before
  field_timeseries_plot(temp_merged, "temp")
```

## test summary

```{r boxplot_temp, fig.width=12, fig.height=4}
  field_boxplot(temp_merged, "temp")
```

# Summary

Temperature was measured for `r length(unique(temp_merged$hh_id))` experiments between `r min(temp_merged$date, na.rm = TRUE)` and `r max(temp_merged$date, na.rm = TRUE)`. There is no temperature data for tests: `r setdiff(as.character(samples$hh_id), as.character(temp_merged$hh_id))`.

Temperature data is expected to be missing for: no tests.

## Save files

* put data into long format

```{r long_data_conversion}
  temp_merged_all <- dplyr::select(temp_merged_all, field_site, hh_id, date, time, datetime, temp, units, qc) %>%
                     tidyr::gather("var", "val", 6)

  temp_merged <- dplyr::select(temp_merged, field_site, hh_id, date, time, datetime, temp, units, qc) %>%
                 tidyr::gather("var", "val", 6)
```

* save data

```{r save_data}
  saveRDS(temp_merged_all, file = "../r_files/field_temp_merged_all.rds")
  saveRDS(temp_merged, file = "../r_files/field_temp_merged.rds")
```
