---
title: "field_sums_flue_analysis"
author: "ricardo_piedrahita"
date: "6/27/2017"
output: html_document
---

## Uses output from field_temp.rmd, field_sums.rmd,montecarlo.rmd
#Analyze SUM vs. flue temperature.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library}
  library(tidyverse)
  library(knitr)
  library(forcats)
```

```{r global_options, include=FALSE}
  knitr::opts_chunk$set(fig.path='figures/', warning=FALSE, message=FALSE)
```

```{r functions}
  source("../r_scripts/plots.r")
  source("../r_scripts/functions.r")
```

# Load data

* flue temperature

```{r load_data}
  fluetemp_merged_all <- readRDS("../r_files/field_temp_merged_all.RDS")
  fluetemp <- readRDS("../r_files/field_temp_merged.RDS")
```

* SUM temperature.  Dug around for additional data for India.

```{r load_data}
  sumtemp_merged_all <- readRDS("../r_files/field_sums_merged_all.RDS")
  sumtemp <- readRDS("../r_files/field_sums.RDS")
```

# Tidy

* Join the data sets after averaging.  Time average the flue temperature so it is on the same basis as the SUM temperatures

```{r time_average}
flue_minute <-  dplyr::group_by(fluetemp_merged_all,hh_id,qc,datetime = cut(datetime, breaks="1 min")) %>%
  dplyr::summarize(val = mean(val)) %>%
  dplyr::mutate(datetime = as.POSIXct(datetime)) %>%
  dplyr::ungroup()

flue_sum_joined <- dplyr::left_join(flue_minute,sumtemp_merged_all,by = c("hh_id", "datetime"))


```

# Plots

## Plot the SUM and flue temperature data independently

```{r plot_all_sum_flue_temp, fig.width=12, fig.height=10}
  field_timeseries_plot(sumtemp_merged_all, "val")
  field_timeseries_plot(fluetemp_merged_all, "val")

```

## Plot the SUM and flue temperature data together to see what we are dealing with.

```{r plot_raw_data,  fig.width=12, fig.height=20}


field_timeseries_plot_hh <- function(df, y_var, y_var2, color_var = "Lascar_Height", x_var = "datetime.x", facet_var = "hh_id", y_units = "units") {
  
 plots<- ggplot(df) +
    geom_line(aes_string(y = y_var, x = x_var, color = color_var)) +
    geom_line(data = df, aes_string(y = y_var2, x = x_var), color = "blue") +
    scale_fill_discrete(drop = FALSE) +
    facet_wrap(~df[[facet_var]], ncol = 1, scales = "free") +
    theme_minimal() +
    theme(legend.position = "top") +
    ylab(paste0(y_var, " (", df[[1, y_units]], ")")) #+
        # geom_line(aes_string(y = y_var2, x = x_var,colour = "Stove_type")) 
      ggsave(plots,filename=paste("figures/CO_emissions_timeseries",y,".png",sep=""))
}
  field_timeseries_plot_co(field_lascarCO_filtered, "val","val")


```


## test summary

```{r boxplot_temp, fig.width=12, fig.height=4}
  field_boxplot(temp_merged, "temp")
```

# Tidy

* Merge SUM and flue temperature data
```{r add_units}
  temp_merged_all <- dplyr::mutate(temp_merged_all, units = "degrees Celsius")
```



# Summary

Temperature was measured for `r length(unique(temp_merged$hh_id))` experiments between `r min(temp_merged$date, na.rm = TRUE)` and `r max(temp_merged$date, na.rm = TRUE)`. There is no temperature data for tests: `r setdiff(as.character(samples$hh_id), as.character(temp_merged$hh_id))`.

Temperature data is expected to be missing for: no tests.

## Save files

* put data into long format

```{r long_data_conversion}
  temp_merged_all <- dplyr::select(temp_merged_all, field_site, hh_id, date, time, datetime, temp, units, qc) %>%
                     tidyr::gather("var", "val", 6)

  temp_merged <- dplyr::select(temp_merged, field_site, hh_id, date, time, datetime, temp, units, qc) %>%
                 tidyr::gather("var", "val", 6)
```

* save data

```{r save_data}
  saveRDS(temp_merged_all, file = "../r_files/field_temp_merged_all.RDS")
  saveRDS(temp_merged, file = "../r_files/field_temp_merged.RDS")
```


