---
title: "Gas analyzer qaqc"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
---

```{r library, message = FALSE, warning = FALSE, echo = FALSE}
  library(tidyverse)
  library(knitr)
  library(lubridate)
```

```{r global_options, include = FALSE}
  knitr::opts_chunk$set(fig.path='figures/', warning = FALSE, message = FALSE)
```

# Load files

* functions

```{r functions}
  source("../r_scripts/functions.R")
  source("../r_scripts/plots.R")
```

* data

```{r load_data}
  aqe <- readRDS("../r_files/field_aqe.RDS")
```

* metadata

```{r load_meta}
  test_times <- readRDS("../r_files/field_test_times.RDS")
  samples <- readRDS("../r_files/field_samples.RDS")
  notes <- readRDS("../r_files/field_compiled_notes.RDS")
```

# Tidy

* fix dates and merge with hh_ids

```{r sample_merge}
  aqe_merged_all <- dplyr::mutate(aqe, date = replace(date, date == "2016-04-25", "2016-04-26")) %>%
                    dplyr::mutate(date = replace(date, date == "2016-04-24", "2016-04-25")) %>%
                    dplyr::mutate(date = replace(date, date == "2016-04-22", "2016-04-23")) %>%
                    dplyr::mutate(date = replace(date, date == "2016-04-21", "2016-04-22")) %>%
                    dplyr::mutate(date = replace(date, date == "2016-04-20", "2016-04-21")) %>%
                    dplyr::mutate(datetime = as.POSIXct(paste(format(date, "%Y-%m-%d"),
                                                              format(datetime, "%H:%M:%S")),
                                                      format = "%Y-%m-%d %H:%M:%S")) %>%
                    dplyr::left_join(dplyr::select(samples, hh_id, field_site, date),
                                     by = "date") %>%
                    dplyr::select(field_site, hh_id, date, time, datetime, co2, co, so2, vocs)
```

* sort by datetime and remove duplicate rows

```{r fix_datetime}
  aqe_merged_all <- dplyr::arrange(aqe_merged_all, datetime) %>%
                    dplyr::distinct() %>%
                    dplyr::filter(!is.na(hh_id)) %>%
                    dplyr::mutate(hh_id = as.factor(hh_id))

```

* set timezones based on field site

```{r fix_timezones}
  aqe_merged_all <- dplyr::mutate(aqe_merged_all,
                                  datetime = lubridate::force_tz(datetime,
                                                                 tzone = "Asia/Calcutta"))
```

* add units

```{r add_units}
  aqe_merged_all <- dplyr::mutate(aqe_merged_all, units = "ppm")
```

# QC

## flags from notes

* extract notes

```{r get_notes}
  notes <- dplyr::filter(notes, grepl("aqe|all", inst) == TRUE)
```

* apply flags: `bad` preceeds `maybe` preceeds `good`

```{r flags}
  flags <- dplyr::select(notes, hh_id, qc) %>%
           dplyr::group_by(hh_id) %>%
           dplyr::arrange(qc) %>%
           dplyr::summarise(qc = first(qc))
```

* merge flags with data

```{r merge_flags}
  # fix warning
  aqe_merged_all <- dplyr::left_join(aqe_merged_all, flags, by = "hh_id") %>%
                    dplyr::mutate(qc = as.factor(ifelse(is.na(qc), "ok", as.character(qc)))) %>%
                    dplyr::mutate(qc = forcats::lvls_expand(qc, c("bad", "maybe", "ok")))
```

## additional bad tests

```{r bad_tests_1}
  #aqe_merged$qc[aqe_merged$hh_id == "IN10"] <- "bad"
```

## Filter only test

```{r get_test_times}
  times <- dplyr::filter(test_times, var == "sample_start" | var == "sample_end") %>%
           tidyr::spread(var, value) %>%
           dplyr::rename(start = sample_start, end = sample_end)
```

```{r filter_test_times}
  aqe_merged <- filter_times(times, aqe_merged_all)
```

## additional bad tests

```{r bad_tests_2}
  #field_temp_merged$qc[field_temp_merged$hh_id == "IN12"] <- "maybe"
  #field_temp_merged$qc[field_temp_merged$hh_id == "IN17"] <- "maybe"
  #field_temp_merged$qc[field_temp_merged$hh_id == "IN18"] <- "maybe"
```

# Calculate background

* Filter pre-background

```{r get_pre_bkgd}
  times <- dplyr::filter(test_times, var == "pre_bkgd_start" | var == "pre_bkgd_end") %>%
           tidyr::spread(var, value) %>%
           dplyr::rename(start = pre_bkgd_start, end = pre_bkgd_end)

  pre_bkgd <- filter_times(times, aqe_merged_all)
```

* Filter post-background

```{r get_post_bkgd}
  times <- dplyr::filter(test_times, var == "post_bkgd_start" | var == "post_bkgd_end") %>%
           tidyr::spread(var, value) %>%
           dplyr::rename(start = post_bkgd_start, end = post_bkgd_end)

  post_bkgd <- filter_times(times, aqe_merged_all)
```

* Combine pre and post bkgd

```{r comb_bkgd}
  aqe_bkgd <- dplyr::bind_rows(pre_bkgd, post_bkgd) %>%
              dplyr::select(-time, -datetime) %>%
              dplyr::group_by(field_site, hh_id, date, units, qc) %>%
              dplyr::summarise_all(funs(mean)) %>%
              dplyr::rename(bkgd_co2 = co2, bkgd_co = co,
                            bkgd_so2 = so2, bkgd_vocs = vocs) %>%
              dplyr::ungroup()
```

* print table
```{r bkgd_table}
  knitr::kable(aqe_bkgd, "markdown", align = 'c', digits = 2)
```

# Plots

## co2

```{r plot_co2, fig.height=10, fig.width=10}
  field_timeseries_plot(aqe_merged, "co2")
```

## boxplot co2

```{r boxplot_co2}
  field_boxplot(aqe_merged, "co2")
```

## co

```{r plot_co, fig.height=10, fig.width=10}
  field_timeseries_plot(aqe_merged, "co")
```

```{r boxplot_co}
  field_boxplot(aqe_merged, "co")
```

## so2

```{r plot_so2, fig.height=10, fig.width=10}
  field_timeseries_plot(aqe_merged, "so2")
```


```{r boxplot_so2}
  field_boxplot(aqe_merged, "so2")
```

## vocs

```{r plot_vocs, fig.height=10, fig.width=10}
  field_timeseries_plot(aqe_merged, "vocs")
```


```{r boxplot_vocs}
  field_boxplot(aqe_merged, "vocs")
```

# Summary

Gas data was measured for `r length(unique(aqe_merged$hh_id))` experiments between `r min(aqe_merged$date, na.rm = TRUE)` and `r max(aqe_merged$date, na.rm = TRUE)`. There is no gas data for tests: `r setdiff(as.character(samples$hh_id), as.character(aqe_merged$hh_id))`.

Some gas data is expected to be missing for IN12.

## Save files

* select relevant columns

```{r select_columns}
  aqe_merged <- dplyr::select(aqe_merged, field_site, hh_id, date, time, datetime,
                              units, qc, co2, bkgd_co2, co, bkgd_co, so2, bkgd_so2,
                              vocs, bkgd_vocs)
```

* save data

```{r save_data}
  saveRDS(aqe_merged, file = "../r_files/field_aqe_merged.RDS")
```
