---
title: "sums"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
---

```{r library, message=FALSE, warning=FALSE, echo=FALSE}
  library(tidyverse)
  library(knitr)
  library(lubridate)
```

```{r global_options, include=FALSE}
  knitr::opts_chunk$set(fig.path='figures/', warning=FALSE, message=FALSE, cache=FALSE)
```

```{r functions}
  source("../r_scripts/functions.R")
  source("../r_scripts/plots.R")
```

# Load data

* flue temperature

```{r load_data}
  sums <- readRDS("../r_files/field_sums.RDS")
```

* metadata

```{r load_meta}
  test_times <- readRDS("../r_files/field_test_times.RDS")
  samples <- readRDS("../r_files/field_samples.RDS")
  temp_meta <- readRDS("../r_files/field_temp_meta.RDS")
  notes <- readRDS("../r_files/field_notes.RDS")
```

# Tidy

* add household id information

```{r add_hh_id}
  sums_all <- dplyr::mutate(sums, logger_id = substring(sums$logger_id, 13, 16)) %>%
                           dplyr::left_join(dplyr::select(temp_meta, logger_id, hh_id, field_site),
                                            by = c("logger_id", "field_site")) %>%
                           dplyr::select(-logger_id)
```

* add units
```{r add_units}
  sums_all <- dplyr::mutate(sums_all, units = "degrees Celsius")
```

# QC

## flags from notes

* extract notes

```{r get_notes}
  notes <- dplyr::filter(notes, grepl("sums|all", inst) == TRUE)
```

* apply flags: `bad` preceeds `maybe` preceeds `good`

```{r flags}
  flags <- dplyr::select(notes, hh_id, qc) %>%
           dplyr::group_by(hh_id) %>%
           dplyr::arrange(qc) %>%
           dplyr::summarise(qc = first(qc))
```

* merge flags with data

```{r merge_flags}
  # fix warning
  sums_all <- dplyr::left_join(sums_all, flags, by = "hh_id") %>%
                           dplyr::mutate(qc = as.factor(ifelse(is.na(qc), "ok", as.character(qc)))) %>%
                           dplyr::mutate(qc = forcats::lvls_expand(qc, c("bad", "maybe", "ok")))
```

## additional bad tests

```{r bad_tests_2}
  sums_all$qc[sums_all$hh_id == "IN4"] <- "maybe"
```

## Filter only test

```{r get_times}
  field_times <- dplyr::filter(test_times, var == "sample_start" | var == "sample_end") %>%
                 tidyr::spread(var, value) %>%
                 dplyr::rename(start = sample_start, end = sample_end)
```

```{r filter_tests}
  # currently missing all data from emissions households
  #field_sums_merged <- filter_times(field_times, sums_all)
```

# Plots

## all data

```{r plot_all_temp_data, fig.width=12, fig.height=20}
  field_timeseries_plot(sums_all, "stove_temp")
```

## data summary

```{r boxplot_temp, fig.width=12, fig.height=4}
  field_boxplot(sums_all, "stove_temp")
```

## test data only

```{r plot_test_temp, fig.width=12, fig.height=10}
  # missing all test day data
  #field_timeseries_plot(field_temp_merged, "temp")
```

# Summary

Temperature was measured for `r length(unique(sums_all$hh_id))` experiments between `r min(sums_all$date, na.rm = TRUE)` and `r max(sums_all$date, na.rm = TRUE)`. There is no temperature data for tests: `r setdiff(as.character(field_samples$hh_id), as.character(sums_all$hh_id))`.

Temperature data is expected to be missing for: no tests.

## Save files

* put data into long format

```{r long_data_conversion}
  sums_all <- dplyr::select(sums_all, field_site, hh_id, date, time, datetime, stove_temp, units, qc) %>%
                           tidyr::gather("var", "val", 6)

  #field_sums_merged <- dplyr::select(field_sums_merged, hh_id, date, time, datetime, stove_temp, units, qc, field_site) %>%
                       #tidyr::gather("var", "val", 5:8)
```

* save data

```{r save_data}
  saveRDS(sums_all, file = "../r_files/sums_all.RDS")
  #saveRDS(field_sums_merged, file = "../r_files/field_sums_merged.RDS")
```
