---
title: "ecoc"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
---

```{r load_libraries, message=FALSE, warning=FALSE, echo=FALSE}
  library(tidyverse)
  library(knitr)
  library(forcats)
```

```{r global_options, include=FALSE}
  knitr::opts_chunk$set(fig.path='figures/', warning=FALSE, message=FALSE, cache=FALSE)
```

```{r load_functions}
  source("../r_scripts/plots.R")
```

# Load data

* ecoc

```{r load_data}
  ecoc <- readRDS("../r_files/field_ecoc.RDS")
```

* metadata

```{r load_meta}
  test_times <- readRDS("../r_files/field_test_times.RDS")
  samples <- readRDS("../r_files/field_samples.RDS")
  notes <- readRDS("../r_files/field_compiled_notes.RDS")
  flows <- readRDS("../r_files/field_inst_flows.RDS")
  filter_meta <- readRDS("../r_files/field_filter_meta.RDS")
```

# Organize

## Filter ecoc data

## Filter meta data

* select only data relevant for grav

```{r filter_meta}
  ecoc_meta <- dplyr::filter(filter_meta, !is.na(quartz_id)) %>%
               dplyr::filter(!grepl("Dummy|Jar Blank|Background", filter_type)) %>%
               dplyr::select(-teflon_id, -cart_type, -hh_id, -notes) %>%
               dplyr::left_join(dplyr::distinct(dplyr::select(test_times, hh_id, date)),
                                by = "date") %>%
               dplyr::mutate(filter_type = fct_drop(filter_type)) %>%  # drop unused factor lvls
               dplyr::mutate(inst = ifelse(grepl("D|E",cart_id), "filter_1", "filter_2")) %>%
               dplyr::mutate(inst = ifelse(filter_type == "Blank", "", inst))
```

## Combine meta data

* calculate average flow rates and combine with test times

```{r meta}
 meta <- dplyr::filter(flows, grepl("filter_1|filter_2", inst)) %>%
         dplyr::select(-notes) %>%  # go off bubble meter measures only
         dplyr::group_by(hh_id, inst) %>%
         dplyr::summarise(avg_flow = mean(val, na.rm = TRUE)) %>%
         dplyr::mutate(filter_type = "Uncontrolled Test") %>%
         dplyr::left_join(tidyr::spread(dplyr::filter(dplyr::select(test_times,
                                                                    -date, -field_site),
                                                      var == "dur"),
                                        var, value),
                          by = "hh_id")
```

## Merge data with meta

```{r meta_merge}
  ecoc <- ecoc %>%
          dplyr::select(-date) %>%
          dplyr::left_join(ecoc_meta, by = c("filter_id" = "quartz_id")) %>%
          dplyr::filter(!is.na(hh_id)) %>%
          dplyr::left_join(meta, by = c("hh_id", "filter_type", "inst"))
```

# QC

* Seperate blanks and samples

```{r seperate_types}
  # currently missing blank filter analysis 
  #blanks <- dplyr::filter(ecoc, filter_type == "Blank")

  ecoc <- dplyr::filter(ecoc, filter_type == "Uncontrolled Test")
```

* extract notes for gravimetric data

```{r extract_notes}
  notes <- dplyr::filter(notes, grepl("ecoc|all", inst) == TRUE)
```

* apply flags: `bad` preceeds `maybe` preceeds `good`

```{r initiate_qc_flags}
  test_flags <- dplyr::filter(notes, !grepl("blanks|Blank", notes)) %>%
                dplyr::select(hh_id, qc) %>%
                dplyr::group_by(hh_id) %>%
                dplyr::arrange(qc) %>%
                dplyr::summarise(qc = first(qc))

  # currently missing blank filter analysis 
  # blank_flags <- dplyr::filter(notes, grepl("blanks|Blank", notes)) %>%
  #                dplyr::select(hh_id, qc) %>%
  #                dplyr::group_by(hh_id) %>%
  #                dplyr::arrange(qc) %>%
  #                dplyr::summarise(qc = first(qc))
```

* merge

```{r add_qc_flag}
  ecoc <- dplyr::left_join(ecoc, test_flags, by = "hh_id") %>%
          dplyr::mutate(id = as.factor(hh_id)) %>%
          dplyr::mutate(qc = as.factor(ifelse(is.na(qc), "ok", as.character(qc))))

  # currently missing blank filter analysis 
  # blanks <- dplyr::left_join(blanks, blank_flags, by = "hh_id") %>%
  #           dplyr::mutate(id = as.factor(hh_id)) %>%
  #           dplyr::mutate(qc = as.factor(ifelse(is.na(qc), "ok", as.character(qc))))
```

* mark additional bad tests

```{r add_bad_tests}
  #blanks$qc[blanks$hh_id == "IN10"] <- "bad"
```

# LOD/LOQ

* calculate the limit of detection and quantification

```{r lod_loq}
  # signal <- dplyr::filter(blanks, qc != "bad") %>%
  #           dplyr::summarise(blank_mean = mean(mass),
  #                            lod = sd(mass) * 3,
  #                            loq = sd(mass) * 10)
  # 
  # blank_mean <- signal$blank_mean[1]
  # lod <- signal$lod[1]
  # loq <- signal$loq[1]
```

The LOD is xx, the LOQ is xx, and the mean of the blanks is xx.

* subract blank mean and flag the measurements

```{r add_lod_loq_var}
  # ecoc <- dplyr::mutate(ecoc, mass = wgt_cal_corr - blank_mean) %>%
  #         dplyr::mutate(lod = ifelse(mass >= lod, "above", "below"),
  #                       loq = ifelse(mass >= loq, "above", "below"))
```

# Background analysis

* need to figure out what to do about background

# Tidy and save

* filter bad tests

```{r filter_bad_tests}
  ecoc <- dplyr::filter(ecoc, qc != "bad")
```

* add pollutant units

```{r add_var}
  ecoc <- ecoc %>%
          dplyr::mutate(units = "micrograms per cm sq")
```

* tidy data for plotting

```{r}
  ecoc_merged <- ecoc %>%
                 dplyr::mutate(filter_type = ifelse(grepl("D|E", cart_id),
                                                    "sample", "artifact")) %>%
                 dplyr::rename(oc = oc_ugsqcm, ec = ec_ugsqcm) %>%
                 dplyr::select(hh_id, date, oc, ec, filter_type,
                               units, avg_flow, dur, qc)
```

# Summary

Ecoc data was collected during `r length(unique(ecoc$hh_id))` experiments between `r min(ecoc$date, na.rm = TRUE)` and `r max(ecoc$date, na.rm = TRUE)`. 

Currently there is no ecoc data for blanks or backgrounds. 

# QC plots

## Sample filters

```{r sample_filters, echo=FALSE}
  p_data <- ecoc_merged %>%
            dplyr::filter(filter_type == "sample")

  field_pointplot(p_data, y_var = "oc")
  
    p_data <- ecoc_merged %>%
            dplyr::filter(filter_type == "sample")
    
  field_pointplot(p_data, y_var = "ec")
```

## Artifact filters

```{r artifact_filters, echo=FALSE}
  p_data <- ecoc_merged %>%
            dplyr::filter(filter_type == "artifact")

  field_pointplot(p_data, y_var = "oc")
  
    p_data <- ecoc_merged %>%
            dplyr::filter(filter_type == "artifact")
    
  field_pointplot(p_data, y_var = "ec")
```

## Blank filters

```{r blanks}
  # p_blanks <- dplyr::filter(blanks, qc != "bad") %>%
  #             dplyr::mutate(units = "micrograms")
  # 
  # field_pointplot(p_blanks, y_var = "mass")
```

* tidy data to save

```{r}
  ecoc_merged <- ecoc_merged %>%
                 dplyr::group_by(hh_id, date, filter_type, qc, units) %>%
                 dplyr::summarise_if(is.numeric, mean) %>%
                 tidyr::gather("var", "val", 6:7)
```

```{r save_data}
  saveRDS(ecoc_merged, file = "../r_files/field_ecoc_merged.RDS")
```
