---
title: "gravimetric"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
---

```{r load_libraries, message=FALSE, warning=FALSE, echo=FALSE}
  library(tidyverse)
  library(knitr)
  library(forcats)
```

```{r global_options, include=FALSE}
  knitr::opts_chunk$set(fig.path='figures/', warning=FALSE, message=FALSE, cache=FALSE)
```

```{r load_functions}
  source("../r_scripts/plots.R")
```

# Load data

* gravimetric

```{r load_data}
  grav <- readRDS("../r_files/field_ecoc.RDS")
```

* metadata

```{r load_meta}
  test_times <- readRDS("../r_files/field_test_times.RDS")
  samples <- readRDS("../r_files/field_samples.RDS")
  notes <- readRDS("../r_files/field_compiled_notes.RDS")
  flows <- readRDS("../r_files/field_inst_flows.RDS")
  filter_meta <- readRDS("../r_files/field_filter_meta.RDS")
```

# Organize

## Filter grav data

* select only filters from emission tests that were used

```{r filter_grav}
  grav <- dplyr::filter(grav, grepl("^IN[0-9]", id))
```

## Filter meta data

* select only data relevant for grav

```{r filter_meta}
  grav_meta <- dplyr::filter(filter_meta, !is.na(teflon_id)) %>%
               dplyr::filter(!grepl("Dummy|Jar Blank|Background", filter_type)) %>%
               dplyr::select(-quartz_id, -cart_type, -hh_id, -notes) %>%
               dplyr::left_join(dplyr::distinct(dplyr::select(test_times, hh_id, date)),
                                by = "date") %>%
               dplyr::mutate(filter_type = fct_drop(filter_type))  # drop unused factor lvls
```

## Combine meta data

* calculate average flow rates and combine with test times

```{r meta}
 meta <- dplyr::filter(flows, inst == "filter_2") %>%
         dplyr::select(-notes) %>%  # go off bubble meter measures only
         dplyr::group_by(hh_id) %>%
         dplyr::summarise(avg_flow = mean(val, na.rm = TRUE)) %>%
         dplyr::mutate(filter_type = "Uncontrolled Test") %>%
         dplyr::left_join(tidyr::spread(dplyr::filter(dplyr::select(test_times,
                                                                    -date, -field_site),
                                                      var == "dur"),
                                        var, value),
                          by = "hh_id")
```

## Merge data with meta

```{r meta_merge}
  grav <- dplyr::left_join(grav, grav_meta, by = c("id" = "teflon_id")) %>%
          dplyr::filter(!is.na(hh_id)) %>%
          dplyr::left_join(meta, by = c("hh_id", "filter_type"))
```

## Calculate weights

* pre-average

```{r calc_pre_wgt}
  grav_pre <- dplyr::select(grav, pre_weigh_1, pre_weigh_2, pre_weigh_3, id) %>%
              tidyr::gather("var", "val", pre_weigh_1, pre_weigh_2, pre_weigh_3) %>%
              dplyr::filter(!is.na(val)) %>%
              dplyr::group_by(id) %>%
              dplyr::summarise(wgt_pre = mean(val))
```

* post-average

```{r calc_post_wgt}
  grav_post <- dplyr::select(grav, post_weigh_1, post_weigh_2, post_weigh_3, id) %>%
               tidyr::gather("var", "val", post_weigh_1, post_weigh_2, post_weigh_3) %>%
               dplyr::filter(!is.na(val)) %>%
               dplyr::group_by(id) %>%
               dplyr::summarise(wgt_post = mean(val))
```

* merge averages

```{r merge_calcs}
  grav <- dplyr::left_join(grav, grav_pre, by = "id") %>%
          dplyr::left_join(grav_post, by = "id")
```

* mass added

```{r calc_delta_wgt}
  grav <- dplyr::mutate(grav, wgt_delta = wgt_post - wgt_pre)
```

* change in calibration weight

```{r add_cal_wgt}
  grav <- dplyr::mutate(grav, wgt_cal_delta = post_cal_weight - pre_cal_weight)
```

# QC

* Seperate blanks and samples

```{r seperate_types}
  blanks <- dplyr::filter(grav, filter_type == "Blank")

  grav <- dplyr::filter(grav, filter_type == "Uncontrolled Test")
```

* extract notes for gravimetric data

```{r extract_notes}
  notes <- dplyr::filter(notes, grepl("grav|all", inst) == TRUE)
```

* apply flags: `bad` preceeds `maybe` preceeds `good`

```{r initiate_qc_flags}
  test_flags <- dplyr::filter(notes, !grepl("blanks|Blank", notes)) %>%
                dplyr::select(hh_id, qc) %>%
                dplyr::group_by(hh_id) %>%
                dplyr::arrange(qc) %>%
                dplyr::summarise(qc = first(qc))

  blank_flags <- dplyr::filter(notes, grepl("blanks|Blank", notes)) %>%
                 dplyr::select(hh_id, qc) %>%
                 dplyr::group_by(hh_id) %>%
                 dplyr::arrange(qc) %>%
                 dplyr::summarise(qc = first(qc))
```

* merge

```{r add_qc_flag}
  grav <- dplyr::left_join(grav, test_flags, by = "hh_id") %>%
          dplyr::mutate(id = as.factor(hh_id)) %>%
          dplyr::mutate(qc = as.factor(ifelse(is.na(qc), "ok", as.character(qc))))

  blanks <- dplyr::left_join(blanks, blank_flags, by = "hh_id") %>%
            dplyr::mutate(id = as.factor(hh_id)) %>%
            dplyr::mutate(qc = as.factor(ifelse(is.na(qc), "ok", as.character(qc))))
```

* mark additional bad tests

```{r add_bad_tests}
  blanks$qc[blanks$hh_id == "IN10"] <- "bad"
  #grav$qc[grav$id == "28B"] <- "bad"
  #grav$qc[grav$id == "29A"] <- "bad"
```

* calibration wgt corrections

```{r calibration_correction}
  grav <- dplyr::mutate(grav, wgt_cal_corr = wgt_delta - wgt_cal_delta)

  blanks <- dplyr::mutate(blanks, mass = wgt_delta - wgt_cal_delta) 
```

# LOD/LOQ

* calculate the limit of detection and quantification

```{r lod_loq}
  signal <- dplyr::filter(blanks, qc != "bad") %>%
            dplyr::summarise(blank_mean = mean(mass),
                             lod = sd(mass) * 3,
                             loq = sd(mass) * 10)

  blank_mean <- signal$blank_mean[1]
  lod <- signal$lod[1]
  loq <- signal$loq[1]
```

The LOD is `r lod`, the LOQ is `r loq`, and the mean of the blanks is `r blank_mean`.

* subract blank mean and flag the measurements

```{r add_lod_loq_var}
  grav <- dplyr::mutate(grav, mass = wgt_cal_corr - blank_mean) %>%
          dplyr::mutate(lod = ifelse(mass >= lod, "above", "below"),
                        loq = ifelse(mass >= loq, "above", "below"))
```

# Background analysis

* need to figure out what to do about background

# Tidy and save

* filter bad tests

```{r filter_bad_tests}
  grav <- dplyr::filter(grav, qc != "bad")
```

* add pollutant variable `pol`

```{r add_var}
  grav <- dplyr::mutate(grav, pol = "pm2.5") %>%
          dplyr::mutate(units = "micrograms")
```

* select variables 

```{r conv_long}
  grav_merged <- dplyr::select(grav, hh_id, date, pol, mass, units, avg_flow, dur, lod, loq, qc)
```

```{r save_data}
  saveRDS(grav_merged, file = "../r_files/field_grav_merged.RDS")
```

# Summary

Gravimetric data was collected during `r length(unique(grav$hh_id))` experiments between `r min(grav$date, na.rm = TRUE)` and `r max(grav$date, na.rm = TRUE)`. 

The gravimetric data from test `r setdiff(as.character(samples$hh_id), as.character(grav$hh_id))` was excluded because the filter was damaged.  

# QC plots

## Sample filters

```{r field_grav}
 field_pointplot(grav, y_var = "mass")
```

## Blank filters

```{r field_grav_blanks}
  p_blanks <- dplyr::filter(blanks, qc != "bad") %>%
              dplyr::mutate(units = "micrograms")

  field_pointplot(p_blanks, y_var = "mass")
```

## Blank cal weights

```{r field_blank_cal_wgt}
  p_cal <- dplyr::mutate(p_blanks, delta_mass = wgt_cal_delta)

  field_pointplot(p_cal, y_var = "delta_mass")
```

## Sample cal weights

```{r field_sample_cal_wgt}
  p_cal <- dplyr::mutate(grav, delta_mass = wgt_cal_delta) %>%
           dplyr::filter(qc != "bad")

  field_pointplot(p_cal, y_var = "delta_mass")
```
