---
title: "Flue temperature - India"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r library, message=FALSE, warning=FALSE, echo=FALSE}
  library(tidyverse)
  library(knitr)
  library(lubridate)
```

```{r global_options, include=FALSE}
  knitr::opts_chunk$set(fig.path='figures/', warning=FALSE, message=FALSE, cache=TRUE)
```

```{r functions}
  source("../r_scripts/functions.R")
  source("../r_scripts/plots.R")
```

# Load data

* flue temperature

```{r load_data}
  temp <- readRDS("../r_files/field_temp.RDS")
```

* metadata

```{r load_meta}
  test_times <- readRDS("../r_files/field_test_times.RDS")
  samples <- readRDS("../r_files/field_samples.RDS")
  temp_meta <- readRDS("../r_files/field_temp_meta.RDS")
```

# Tidy

* add household id information

```{r add_hh_id}
  temp_merged_all <- dplyr::left_join(temp, dplyr::select(temp_meta %>%
                                                            dplyr::filter(field_site == "india"),
                                                          logger_id, hh_id, field_site),
                                            by = "logger_id") %>%
                     dplyr::select(-logger_id)
```

```{r}
  temp_merged_all <- 
    temp_merged_all %>%
    #dplyr::group_by(datetime, hh_id) %>%
    dplyr::group_by(datetime = cut(datetime, breaks = "1 min"), hh_id) %>%
    dplyr::summarise(temp = mean(temp)) %>%
    dplyr::ungroup()
```

* fix India times

```{r fix_times}
  temp_merged_all <- 
    temp_merged_all %>%
    dplyr::mutate(datetime = as.POSIXct(datetime),
                  datetime = with_tz(datetime, tz = "Asia/Calcutta"),
                  date = as.Date(datetime),
                  time = as.numeric(hms(format(datetime, "%H:%M:%S"))))
```

# QC

## merge flags with data

```{r merge_flags}
  # fix warning
  temp_merged_all <- 
    temp_merged_all %>%
    dplyr::mutate(qc = "ok")
```

```{r}
  temp_merged_all <-
    temp_merged_all %>%
    dplyr::filter(!(hh_id == "IN11" & date == "2016-04-20" & time < 36900),
                  !(hh_id == "IN11" & date == "2016-05-15"),
                  !(hh_id == "IN11" & date == "2016-05-16"),
                  !(hh_id == "IN11" & date == "2016-05-17"),
                  !(hh_id == "IN11" & date == "2016-05-18"),
                  !(hh_id == "IN11" & date == "2016-05-19"),
                  !(hh_id == "IN11" & date == "2016-05-20"))
```

```{r, eval=FALSE}
  diff <- rep(NA, nrow(temp_merged_all))
  diff[2:nrow(temp_merged_all)] <- diff(temp_merged_all$temp)
  
  temp_merged_all <-
    temp_merged_all %>%
    dplyr::bind_cols(data.frame(diff)) %>%
    dplyr::filter(diff < 50)
```

```{r, eval=FALSE}
  temp_merged %>%
  ggplot(aes(x = datetime, y = temp)) +
    geom_line() +
    facet_wrap(~hh_id, scales = "free")
```

## Filter only test

```{r get_times}
  times <- dplyr::filter(test_times, var == "sample_start" | var == "sample_end") %>%
           tidyr::spread(var, value) %>%
           dplyr::rename(start = sample_start, end = sample_end)
```

```{r filter_tests}
  temp_merged <- filter_times(times, temp_merged_all)
```

# remove bad data

```{r}
  temp_merged <-
    temp_merged %>%
    dplyr::filter(!(hh_id == "IN19"))
```

# Plots

## all data

```{r plot_all_temp_data, fig.width=12, fig.height=10, eval=FALSE}
  field_timeseries_plot(temp_merged_all, "temp")
```

## test data only

```{r plot_test_temp, fig.width=8, fig.height=10}
  # duplicates coming in before
  field_timeseries_plot(temp_merged, "temp")
```

## test summary

```{r boxplot_temp, fig.width=8, fig.height=4}
  field_boxplot(temp_merged, "temp")
```

# Summary

Temperature was measured for `r length(unique(temp_merged$hh_id))` experiments between `r min(temp_merged$date, na.rm = TRUE)` and `r max(temp_merged$date, na.rm = TRUE)`. There is no temperature data for tests: `r setdiff(as.character(samples$hh_id), as.character(temp_merged$hh_id))`.

Temperature data is expected to be missing for: no tests.

## Save files

* put data into long format

```{r long_data_conversion}
  temp_merged_all <- dplyr::select(temp_merged_all, hh_id, date, time, datetime, temp, qc) %>%
                     dplyr::mutate(field_site = "India")

  temp_merged <- dplyr::select(temp_merged, hh_id, date, time, datetime, temp, qc) %>%
                     dplyr::mutate(field_site = "India")
```

* save data

```{r save_data}
  saveRDS(temp_merged_all, file = "../r_files/india_temp_merged_all.RDS")
  saveRDS(temp_merged, file = "../r_files/india_temp_merged.RDS")
```
