---
title: "Black carbon analyzer qaqc"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
---

```{r library, message = FALSE, warning = FALSE, echo = FALSE}
  library(tidyverse)
  library(knitr)
  library(lubridate)
```

```{r global_options, include = FALSE}
  knitr::opts_chunk$set(fig.path='figures/', warning = FALSE, message = FALSE)
```

# Load files

* functions

```{r functions}
  source("../r_scripts/functions.R")
  source("../r_scripts/plots.R")
```

* data

```{r load_data}
  ma <- readRDS("../r_files/field_ma.RDS")
```

* metadata

```{r load_meta}
  test_times <- readRDS("../r_files/field_test_times.RDS")
  samples <- readRDS("../r_files/field_samples.RDS")
  notes <- readRDS("../r_files/field_compiled_notes.RDS")
```

# Tidy

* fix dates and merge with hh_ids

```{r sample_merge}
  ma_merged_all <- ma %>%
                    dplyr::left_join(dplyr::select(samples, hh_id, field_site, date),
                                     by = "date")
```

* sort by datetime and remove duplicate rows

```{r fix_datetime}
  ma_merged_all <- ma_merged_all %>%
                   dplyr::arrange(datetime) %>%
                   dplyr::distinct() %>%
                   dplyr::filter(!is.na(hh_id)) %>%
                   dplyr::mutate(hh_id = as.factor(hh_id))

```

* set timezones based on field site

```{r fix_timezones}
  ma_merged_all <- ma_merged_all %>%
                   dplyr::mutate(datetime = lubridate::force_tz(datetime,
                                                                tzone = "Asia/Calcutta"))
```

* add units

```{r add_units}
  ma_merged_all <- ma_merged_all %>%
                   dplyr::mutate(units = "nanograms per meter cubed")
```

# QC

## flags from notes

* extract notes

```{r get_notes}
  notes <- dplyr::filter(notes, grepl("microaeth|all", inst) == TRUE)
```

* apply flags: `bad` preceeds `maybe` preceeds `good`

```{r flags}
  flags <- dplyr::select(notes, hh_id, qc) %>%
           dplyr::group_by(hh_id) %>%
           dplyr::arrange(qc) %>%
           dplyr::summarise(qc = first(qc))
```

* merge flags with data

```{r merge_flags}
  # fix warning
  ma_merged_all <- ma_merged_all %>%
                   dplyr::left_join(flags, by = "hh_id") %>%
                   dplyr::mutate(qc = as.factor(ifelse(is.na(qc), "ok", as.character(qc)))) %>%
                   dplyr::mutate(qc = forcats::lvls_expand(qc, c("bad", "maybe", "ok")))
```

## additional bad tests

```{r bad_tests_1}
  #aqe_merged$qc[aqe_merged$hh_id == "IN10"] <- "bad"
```

## Filter only test

```{r get_test_times}
  times <- test_times %>%
           dplyr::filter(var == "sample_start" | var == "sample_end") %>%
           tidyr::spread("var", "val") %>%
           dplyr::rename(start = sample_start, end = sample_end)
```

```{r filter_test_times}
  aqe_merged <- filter_times(times, aqe_merged_all)
```

## additional bad tests

```{r bad_tests_2}
  #field_temp_merged$qc[field_temp_merged$hh_id == "IN12"] <- "maybe"
  #field_temp_merged$qc[field_temp_merged$hh_id == "IN17"] <- "maybe"
  #field_temp_merged$qc[field_temp_merged$hh_id == "IN18"] <- "maybe"
```

# Calculate background

* Filter pre-background

```{r get_pre_bkgd}
  times <- dplyr::filter(test_times, var == "pre_bkgd_start" | var == "pre_bkgd_end") %>%
           tidyr::spread(var, value) %>%
           dplyr::rename(start = pre_bkgd_start, end = pre_bkgd_end)

  pre_bkgd <- filter_times(times, aqe_merged_all)
```

* Filter post-background

```{r get_post_bkgd}
  times <- dplyr::filter(test_times, var == "post_bkgd_start" | var == "post_bkgd_end") %>%
           tidyr::spread(var, value) %>%
           dplyr::rename(start = post_bkgd_start, end = post_bkgd_end)

  post_bkgd <- filter_times(times, aqe_merged_all)
```

* Combine pre and post bkgd

```{r comb_bkgd}
  bkgd <- dplyr::bind_rows(pre_bkgd, post_bkgd)
```

* Calculate background mean

```{r calc_mean}
  bkgd_mean <- dplyr::bind_rows(pre_bkgd, post_bkgd) %>%
               dplyr::group_by(field_site, hh_id, date, units, qc) %>%
               dplyr::summarise_all(funs(mean)) %>%
               dplyr::select(-time, -datetime) %>%
               dplyr::ungroup()
```

* Print table

```{r bkgd_table}
  knitr::kable(bkgd_mean, "markdown", align = 'c', digits = 2)
```

# Plots

## co2

```{r plot_co2, fig.height=10, fig.width=10}
  field_timeseries_plot(aqe_merged, "co2")
```

## boxplot co2

```{r boxplot_co2}
  field_boxplot(aqe_merged, "co2")
```

## co

```{r plot_co, fig.height=10, fig.width=10}
  field_timeseries_plot(aqe_merged, "co")
```

```{r boxplot_co}
  field_boxplot(aqe_merged, "co")
```

## so2

```{r plot_so2, fig.height=10, fig.width=10}
  field_timeseries_plot(aqe_merged, "so2")
```


```{r boxplot_so2}
  field_boxplot(aqe_merged, "so2")
```

## vocs

```{r plot_vocs, fig.height=10, fig.width=10}
  field_timeseries_plot(aqe_merged, "vocs")
```


```{r boxplot_vocs}
  field_boxplot(aqe_merged, "vocs")
```

# Summary

Gas data was measured for `r length(unique(aqe_merged$hh_id))` experiments between `r min(aqe_merged$date, na.rm = TRUE)` and `r max(aqe_merged$date, na.rm = TRUE)`. There is no gas data for tests: `r setdiff(as.character(samples$hh_id), as.character(aqe_merged$hh_id))`.

Some gas data is expected to be missing for IN12.

## Save files

* convert merged emissions file to long format

```{r long_data}
  aqe_merged <- tidyr::gather(aqe_merged, "var", "val", 6:9)
```

```{r long_bkgd}
  bkgd <- tidyr::gather(bkgd, "var", "val", 6:9)

  bkgd_mean <- tidyr::gather(bkgd_mean, "var", "val", 6:9)
```

* Create list object for bkgd data

```{r bkgd_list}
  aqe_bkgd <- list(bkgd = bkgd, mean = bkgd_mean)
```

* save data

```{r save_data}
  saveRDS(aqe_merged, file = "../r_files/field_aqe_merged.RDS")
  saveRDS(aqe_bkgd, file = "../r_files/field_aqe_bkgd.RDS")
```
