---
title: "Figure 2 for Firepower Sweep Paper"
output:
  html_document:
    toc: true
    toc_float: true
    theme: paper
---

```{r load_libraries, echo=FALSE, message=FALSE}
  library(tidyverse)
```

```{r global_options, include=FALSE}
  knitr::opts_chunk$set(fig.path='figures/', warning=FALSE, message=FALSE, cache=FALSE, echo=FALSE)
```

```{r load_data}
  grav <- readRDS("../r_files/lab_grav_merged.RDS")
```

```{r}
  grav <-
    grav %>%
    dplyr::filter(id != "3B", fuel != "okote")
```

```{r fig_2a, fig.width=10, fig.height=6}
  grav %>%
    dplyr::filter(grepl("fp|mce", var), grepl("continuous", fst_type)) %>%
    dplyr::select(-units) %>%
    tidyr::spread(var, val) %>%
                  dplyr::mutate(protocol = as.character(sample_id),
                                protocol = ifelse(grepl("start_up", sample_id), "start-up", protocol),
                                protocol = ifelse(grepl("shutdown", sample_id), "shut-down", protocol),
                                protocol = ifelse(grepl("1|2|3|4", sample_id), "phase one", protocol),
                                protocol = ifelse(grepl("5|6|7", sample_id), "phase two", protocol)) %>%
                   dplyr::mutate(protocol = forcats::fct_relevel(protocol,
                                                             "start-up",
                                                             "phase one",
                                                             "phase two",
                                                             "shut-down"),
                                 stove = forcats::fct_relevel(stove,
                                                              "three stone fire^{1}",
                                                              "mud chulha^{1}",
                                                              "metal grill^{1}",
                                                              "rocket elbow^{2}",
                                                              "ceramic plancha^{3}",
                                                              "metal plancha^{3}")) %>%
    ggplot(aes(x = fp, y = mce, shape = protocol, color = fuel)) +
    geom_point(size = 3, alpha = 0.75, stroke = 1) +
    scale_color_manual(values = c("#999999", "#E69F00")) +
    scale_shape_manual(values = c(8, 1, 16, 4)) +
    guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.75))) +
      theme_bw() + 
      theme(text = element_text(size = 14),
            strip.text.x = element_text(size = 16),
            strip.background = element_rect(fill = "white"),
            plot.title = element_text(hjust = 0.5),
            legend.position = "right") +
      facet_wrap(~stove, nrow = 2) +
      ggtitle("Continuous-Feed Wood Stoves") +
      scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14)) +
      xlab("Firepower (kW)") +
      ylab("MCE") +
      labs(shape = "Fuel", color = "Protocol")
```

```{r fig_2b, fig.width=10, fig.height=3.5}
  grav %>%
    dplyr::filter(grepl("fp|mce", var), grepl("batch", fst_type)) %>%
    dplyr::select(-units) %>%
    tidyr::spread(var, val) %>%
                  dplyr::mutate(protocol = as.character(sample_id),
                                protocol = ifelse(grepl("start_up", sample_id), "start-up", protocol),
                                protocol = ifelse(grepl("shutdown", sample_id), "shut-down", protocol),
                                protocol = ifelse(grepl("3", sample_id), "relight and restart", protocol),
                                protocol = ifelse(grepl("1|2", sample_id), "phase one", protocol),
                                protocol = ifelse(grepl("4|5", sample_id), "phase two", protocol)) %>%
               dplyr::mutate(stove = forcats::fct_relevel(stove,
                                              "ceramic jiko",
                                              "metal jiko",
                                              "forced draft gasifier")) %>%
    dplyr::mutate(fuel = forcats::fct_relevel(fuel,
                                              "coconut charcoal",
                                              "hardwood charcoal",
                                              "eucalyptus (pellets)",
                                              "red oak (milled)")) %>%
               dplyr::mutate(protocol = forcats::fct_relevel(protocol,
                                                             "start-up",
                                                             "phase one",
                                                             "relight and restart",
                                                             "phase two",
                                                             "shut-down")) %>%
    ggplot(aes(x = fp, y = mce, color = fuel, shape = protocol)) +
    geom_point(alpha = 0.75, size = 3, stroke = 1) +
    scale_color_manual(values = c("#7b3294", "#c2a5cf", "#a6dba0", "#008837")) +
    guides(color = guide_legend(override.aes = list(size = 3))) +
    scale_shape_manual(values = c(8, 1, 3, 16, 4)) +
      theme_bw() + 
      theme(text = element_text(size = 14),
            strip.text.x = element_text(size = 16),
            strip.background = element_rect(fill = "white"),
            plot.title = element_text(hjust = 0.5),
            legend.position = "right") +
      facet_wrap(~stove, nrow = 1) +
      ggtitle("Batch-Fed Stoves") +
      xlab("Firepower (kW)") +
      ylab("MCE") +
      labs(color = "Protocol", shape = "Fuel")
```

# Stoves

```{r}
  continuous <- 
    grav %>%
    dplyr::filter(grepl("fp|mce", var), grepl("continuous", fst_type)) %>%
    dplyr::select(-units) %>%
    tidyr::spread(var, val)
```

* The minimum firepower achieved by continuous-feed wood stoves was: `r min(continuous$fp)`.
* The maximum firepower achieved by continuous-feed wood stoves was: `r max(continuous$fp)`.
* The minimum mce achieved by continuous-feed wood stoves was: `r min(continuous$mce)`.
* The minimum mce achieved by continuous-feed wood stoves was: `r max(continuous$mce)`.

```{r}
  batch <- 
    grav %>%
    dplyr::filter(grepl("fp|mce", var), grepl("batch", fst_type)) %>%
    dplyr::select(-units) %>%
    tidyr::spread(var, val)
```

```{r}
  batch_charcoal <- 
    grav %>%
    dplyr::filter(grepl("fp|mce", var), grepl("batch", fst_type)) %>%
    dplyr::select(-units) %>%
    tidyr::spread(var, val)
```

* The minimum firepower achieved by batch-fed charcoal stoves was: `r min(batch_charcoal$fp)`.
* The maximum firepower achieved by batch-fed charcoal wood stoves was: `r max(batch_charcoal$fp)`.
* The minimum mce achieved by batch-fed charcoal stoves was: `r min(batch_charcoal$mce)`.
* The minimum mce achieved by batch-fed charcoal stoves was: `r max(batch_charcoal$mce)`.

```{r}
  batch_gasifier <- 
    grav %>%
    dplyr::filter(grepl("fp|mce", var), grepl("batch", fst_type)) %>%
    dplyr::select(-units) %>%
    tidyr::spread(var, val)
```

* The minimum firepower achieved by gasifier stoves was: `r min(batch_gasifier$fp)`.
* The maximum firepower achieved by gasifier stoves was: `r max(batch_gasifier$fp)`.
* The minimum mce achieved by gasifier stoves was: `r min(batch_gasifier$mce)`.
* The minimum mce achieved by gasifierstoves was: `r max(batch_gasifier$mce)`.

```{r}
  continuous %>%
    dplyr::group_by(stove) %>%
    dplyr::summarise(min_fp = min(fp),
                     max_fp = max(fp),
                     min_mce = min(mce),
                     max_mce = max(mce),
                     mean_fp = mean(fp),
                     mean_mce = mean(mce)) %>%
    dplyr::mutate(diff_fp = max_fp - min_fp,
                  diff_mce = max_mce - min_mce) %>%
  knitr::kable()
```

```{r}
  continuous %>%
    dplyr::group_by(stove_cat) %>%
    dplyr::summarise(min_fp = min(fp),
                     max_fp = max(fp),
                     min_mce = min(mce),
                     max_mce = max(mce),
                     mean_fp = mean(fp),
                     mean_mce = mean(mce)) %>%
    dplyr::mutate(diff_fp = max_fp - min_fp,
                  diff_mce = max_mce - min_mce) %>%
  knitr::kable()
```

```{r}
  batch %>%
    dplyr::group_by(stove) %>%
    dplyr::summarise(min_fp = min(fp),
                     max_fp = max(fp),
                     min_mce = min(mce),
                     max_mce = max(mce),
                     mean_fp = mean(fp),
                     mean_mce = mean(mce)) %>%
    dplyr::mutate(diff_fp = max_fp - min_fp,
                  diff_mce = max_mce - min_mce) %>%
  knitr::kable()
```

# Fuels

only looking at stoves tested with both fuels

```{r}
  continuous %>%
    dplyr::group_by(fuel) %>%
    dplyr::filter(!grepl("plancha", stove), !grepl("21", id)) %>%
    dplyr::summarise(min_fp = min(fp),
                     max_fp = max(fp),
                     min_mce = min(mce),
                     max_mce = max(mce),
                     mean_fp = mean(fp),
                     mean_mce = mean(mce)) %>%
    dplyr::mutate(diff_fp = max_fp - min_fp,
                  diff_mce = max_mce - min_mce) %>%
  knitr::kable()
```

```{r}
  batch %>%
    dplyr::group_by(fuel) %>%
        dplyr::filter(grepl("8|9|10|11|22|24", id)) %>%
    dplyr::summarise(min_fp = min(fp),
                     max_fp = max(fp),
                     min_mce = min(mce),
                     max_mce = max(mce),
                     mean_fp = mean(fp),
                     mean_mce = mean(mce)) %>%
    dplyr::mutate(diff_fp = max_fp - min_fp,
                  diff_mce = max_mce - min_mce) %>%
  knitr::kable()
```