---
title: "Figure 2 for Firepower Sweep Paper"
output:
  html_document:
    toc: true
    toc_float: true
    theme: paper
---

```{r load_libraries, echo=FALSE, message=FALSE}
  library(tidyverse)
```

```{r global_options, include=FALSE}
  knitr::opts_chunk$set(fig.path='figures/', warning=FALSE, message=FALSE, cache=FALSE, echo=FALSE)
```

```{r load_data}
  grav <- readRDS("../r_files/lab_grav_merged.RDS")
  wbt <- readRDS("../r_files/wbt_data_merged.RDS")
```

```{r}
  grav <-
    grav %>%
    dplyr::filter(id != "3B", fuel != "okote")
```

```{r}
  continuous <- 
    grav %>%
    dplyr::filter(grepl("fp|mce", var), grepl("continuous", fst_type)) %>%
    dplyr::select(-units) %>%
    tidyr::spread(var, val) %>%
    dplyr::mutate(phase = as.character(sample_id),
                  phase = ifelse(grepl("start_up", sample_id), "FST: start-up", phase),
                  phase = ifelse(grepl("shutdown", sample_id), "FST: shut-down", phase),
                  phase = ifelse(grepl("1|2|3|4", sample_id), "FST: sweep-down", phase),
                  phase = ifelse(grepl("5|6|7", sample_id), "FST: sweep-up", phase),
                  phase = forcats::fct_expand(as_factor(phase), "WBT: high power", "WBT: low power"),
                  phase = as_factor(phase,
                                    levels = c("FST: start-up",
                                               "FST: sweep-down",
                                               "FST: sweep-up",
                                               "FST: shut-down",
                                               "WBT: high power",
                                               "WBT: low power"),
                                    ordered = TRUE),
                  stove = forcats::fct_relevel(stove,
                                               "three stone fire",
                                               "mud chulha",
                                               "metal grill",
                                               "rocket elbow",
                                               "ceramic plancha",
                                               "metal plancha"))
```

```{r}
  batch <- 
    grav %>%
    dplyr::filter(grepl("fp|mce", var), grepl("batch", fst_type)) %>%
    dplyr::select(-units) %>%
    tidyr::spread(var, val) %>%
    dplyr::mutate(phase = as.character(sample_id),
                  phase = ifelse(grepl("start_up", sample_id), "FST: start-up", phase),
                  phase = ifelse(grepl("shutdown", sample_id), "FST: shut-down", phase),
                  phase = ifelse(grepl("3", sample_id), "FST: refuel", phase),
                  phase = ifelse(grepl("1|2", sample_id), "FST: pre-refuel", phase),
                  phase = ifelse(grepl("4|5", sample_id), "FST: post-refuel", phase),
                  phase = as_factor(phase,
                                    levels = c("FST: start-up",
                                               "FST: pre-refuel",
                                               "FST: refuel",
                                               "FST: post-refuel",
                                               "FST: shut-down",
                                               "WBT: high power",
                                               "WBT: low power"),
                                    ordered = TRUE),
                  stove = forcats::fct_relevel(stove,
                                               "ceramic jiko",
                                               "metal jiko",
                                               "forced draft gasifier"),
                  fuel = forcats::fct_relevel(fuel,
                                              "coconut charcoal",
                                              "hardwood charcoal",
                                              "eucalyptus (pellets)",
                                              "red oak (milled)"),
                  phase = forcats::fct_relevel(phase,
                                               "FST: start-up",
                                               "FST: pre-refuel",
                                               "FST: refuel",
                                               "FST: post-refuel",
                                               "FST: shut-down",
                                               "WBT: high power",
                                               "WBT: low power"))
```

```{r}
  wbt_plot <-
    wbt %>%
    dplyr::filter(grepl("firepower", pol)) %>%
    dplyr::mutate(value = ifelse(units == "watts", value / 1000, value)) %>%
    tidyr::spread(var, value) %>%
    dplyr::mutate(fp_min = mean - stdev, fp_max = mean + stdev) %>%
    dplyr::rename("firepower" = "mean") %>%
    dplyr::select(-stdev, -pol, -units) %>%
    dplyr::left_join(wbt %>%
                     dplyr::select(id, stove, fuel, pol, var, value,
                                   fuel_notes, protocol, protocol_notes) %>%
                     dplyr::filter(grepl("mce", pol)) %>%
                     tidyr::spread(var, value) %>%
                     dplyr::mutate(mce_min = mean - stdev, mce_max = mean + stdev) %>%
                     dplyr::rename("mce" = "mean") %>%
                     dplyr::select(-stdev, -pol),
                     by = c("id", "protocol", "stove", "fuel", "fuel_notes", "protocol_notes")) %>%
    dplyr::filter(fuel_notes != "wet", grepl("three|metal jiko|rocket|forced|plancha|ceramic jiko", stove)) %>%
    dplyr::mutate(phase = ifelse(grepl("simmer", protocol), "WBT: low power", "WBT: high power"))
```

```{r}
  wbt_cont <-
    wbt_plot %>%
    dplyr::filter(grepl("continuous", fst_type))
    

  wbt_batch <-
    wbt_plot %>%
    dplyr::filter(grepl("batch", fst_type))
```

# Plots

```{r fig_2a, fig.width=10, fig.height=6}
  continuous %>%
    ggplot(aes(x = fp, y = mce, shape = phase, color = fuel)) +
      geom_point(size = 3, alpha = 0.75, stroke = 1) +
      geom_point(data = wbt_cont,
                 aes(x = firepower, y = mce, shape = phase),
                 size = 3, stroke = 1, color = "black") +
      #geom_errorbar(data = wbt_cont, aes(x = firepower, y = mce,
      #                                   ymin = mce_min, ymax = mce_max),
      #              width = 0, color = "black") +
      #geom_errorbarh(data = wbt_cont, aes(x = firepower, y = mce,
      #                                    xmin = fp_min, xmax = fp_max),
      #              height = 0, color = "black") +
      scale_color_manual(values = c("#999999", "#E69F00")) +
      scale_shape_manual(values = c(8, 1, 16, 4, 0, 2)) +
      guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.75))) +
      theme_bw() + 
      theme(text = element_text(size = 16),
            strip.text.x = element_text(size = 16),
            strip.background = element_rect(fill = "white"),
            plot.title = element_text(hjust = 0.5),
            legend.position = "right") +
        facet_wrap(~ stove, nrow = 2) +
        ggtitle("Continuous-Feed Wood Stoves") +
        scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14)) +
        xlab("Firepower (kW)") +
        ylab("MCE") +
        labs(shape = "", color = "")
```

```{r fig_2b, fig.width=10, fig.height=3.5}
  batch %>%
    ggplot(aes(x = fp, y = mce, color = fuel, shape = phase)) +
      geom_point(alpha = 0.75, size = 3, stroke = 1) +
      geom_point(data = wbt_batch, aes(x = firepower, y = mce, shape = phase),
                 size = 3, stroke = 1, color = "black") +
      geom_errorbar(data = wbt_batch, aes(x = firepower, y = mce,
                                         ymin = mce_min, ymax = mce_max),
                    width = 0, color = "black") +
      geom_errorbarh(data = wbt_batch, aes(x = firepower, y = mce,
                                          xmin = fp_min, xmax = fp_max),
                    height = 0, color = "black") +
      scale_color_manual(values = c("#7b3294", "#c2a5cf", "#a6dba0", "#008837")) +
      guides(color = guide_legend(override.aes = list(size = 3))) +
      scale_shape_manual(values = c(8, 1, 3, 16, 4, 0, 2)) +
      theme_bw() + 
      theme(text = element_text(size = 16),
            strip.text.x = element_text(size = 16),
            strip.background = element_rect(fill = "white"),
            plot.title = element_text(hjust = 0.5),
            legend.position = "right") +
        facet_wrap(~stove, nrow = 1) +
        ggtitle("Batch-Fed Stoves") +
        xlab("Firepower (kW)") +
        ylab("MCE") +
        labs(color = "", shape = "")
```

# Statistics by test type

```{r}
  batch_charcoal <- 
    batch %>%
    dplyr::filter(grepl("coconut|hardwood", fuel))
```

```{r}
  batch_gasifier <- 
    batch %>%
    dplyr::filter(!grepl("coconut|hardwood", fuel))
```

## Continuous-feed wood stoves

```{r}
  continuous %>%
    dplyr::summarise(min_fp = min(fp),
                     max_fp = max(fp),
                     min_mce = min(mce),
                     max_mce = max(mce),
                     mean_fp = mean(fp),
                     mean_mce = mean(mce),
                     stdev_fp = sd(fp),
                     stdev_mce = sd(mce)) %>%
    dplyr::mutate(range_fp = max_fp - min_fp,
                  range_mce = max_mce - min_mce) %>%
    knitr::kable()
```

## Batch-fed charcoal stoves

```{r}
  batch_charcoal %>%
    dplyr::summarise(min_fp = min(fp),
                     max_fp = max(fp),
                     min_mce = min(mce),
                     max_mce = max(mce),
                     mean_fp = mean(fp),
                     mean_mce = mean(mce),
                     stdev_fp = sd(fp),
                     stdev_mce = sd(mce)) %>%
    dplyr::mutate(range_fp = max_fp - min_fp,
                  range_mce = max_mce - min_mce) %>%
    knitr::kable()
```

## Batch-fed wood stoves

```{r}
  batch_gasifier %>%
    dplyr::summarise(min_fp = min(fp),
                     max_fp = max(fp),
                     min_mce = min(mce),
                     max_mce = max(mce),
                     mean_fp = mean(fp),
                     mean_mce = mean(mce),
                     stdev_fp = sd(fp),
                     stdev_mce = sd(mce)) %>%
    dplyr::mutate(range_fp = max_fp - min_fp,
                  range_mce = max_mce - min_mce) %>%
    knitr::kable()
```

# Statistics by stove type and stove category

## Continuous-feed wood stoves

```{r}
  continuous %>%
    dplyr::group_by(stove) %>%
    dplyr::summarise(min_fp = min(fp),
                     max_fp = max(fp),
                     min_mce = min(mce),
                     max_mce = max(mce),
                     mean_fp = mean(fp),
                     mean_mce = mean(mce),
                     stdev_fp = sd(fp),
                     stdev_mce = sd(mce)) %>%
    dplyr::mutate(range_fp = max_fp - min_fp,
                  range_mce = max_mce - min_mce) %>%
    knitr::kable()
```

```{r}
  continuous %>%
    dplyr::group_by(stove_cat) %>%
    dplyr::summarise(min_fp = min(fp),
                     max_fp = max(fp),
                     min_mce = min(mce),
                     max_mce = max(mce),
                     mean_fp = mean(fp),
                     mean_mce = mean(mce),
                     stdev_fp = sd(fp),
                     stdev_mce = sd(mce)) %>%
    dplyr::mutate(range_fp = max_fp - min_fp,
                  range_mce = max_mce - min_mce) %>%
    knitr::kable()
```

## Batch-fed stoves

```{r}
  batch %>%
    dplyr::group_by(stove) %>%
    dplyr::summarise(min_fp = min(fp),
                     max_fp = max(fp),
                     min_mce = min(mce),
                     max_mce = max(mce),
                     mean_fp = mean(fp),
                     mean_mce = mean(mce),
                     stdev_fp = sd(fp),
                     stdev_mce = sd(mce)) %>%
    dplyr::mutate(range_fp = max_fp - min_fp,
                  range_mce = max_mce - min_mce) %>%
    knitr::kable()
```

# Statistics by fuel type

* Only looking at stoves tested with both fuels were selected

## Continuous-feed wood stoves

```{r}
  continuous %>%
    dplyr::group_by(fuel) %>%
    dplyr::filter(!grepl("plancha", stove), !grepl("21", id)) %>%
    dplyr::summarise(min_fp = min(fp),
                     max_fp = max(fp),
                     min_mce = min(mce),
                     max_mce = max(mce),
                     mean_fp = mean(fp),
                     mean_mce = mean(mce),
                     stdev_fp = sd(fp),
                     stdev_mce = sd(mce)) %>%
    dplyr::mutate(range_fp = max_fp - min_fp,
                  range_mce = max_mce - min_mce) %>%
    knitr::kable()
```

## Batch-fed stoves

```{r}
  batch %>%
    dplyr::group_by(fuel) %>%
    dplyr::filter(grepl("8|9|10|11|22|24", id)) %>%
    dplyr::summarise(min_fp = min(fp),
                     max_fp = max(fp),
                     min_mce = min(mce),
                     max_mce = max(mce),
                     mean_fp = mean(fp),
                     mean_mce = mean(mce),
                     stdev_fp = sd(fp),
                     stdev_mce = sd(mce)) %>%
    dplyr::mutate(range_fp = max_fp - min_fp,
                  range_mce = max_mce - min_mce) %>%
    knitr::kable()
```

# Statistics by test phase

## Continuous-feed wood stoves

```{r}
  continuous %>%
    dplyr::group_by(phase) %>%
    dplyr::summarise(min_fp = min(fp),
                     max_fp = max(fp),
                     min_mce = min(mce),
                     max_mce = max(mce),
                     mean_fp = mean(fp),
                     mean_mce = mean(mce),
                     stdev_fp = sd(fp),
                     stdev_mce = sd(mce)) %>%
    dplyr::mutate(range_fp = max_fp - min_fp,
                  range_mce = max_mce - min_mce) %>%
    knitr::kable()
```

## Batch-fed charcoal stoves

```{r}
  batch_charcoal %>%
    dplyr::group_by(phase) %>%
    dplyr::summarise(min_fp = min(fp),
                     max_fp = max(fp),
                     min_mce = min(mce),
                     max_mce = max(mce),
                     mean_fp = mean(fp),
                     mean_mce = mean(mce),
                     stdev_fp = sd(fp),
                     stdev_mce = sd(mce)) %>%
    dplyr::mutate(range_fp = max_fp - min_fp,
                  range_mce = max_mce - min_mce) %>%
    knitr::kable()
```

## Batch-fed wood stoves

```{r}
  batch_gasifier %>%
    dplyr::group_by(phase) %>%
    dplyr::summarise(min_fp = min(fp),
                     max_fp = max(fp),
                     min_mce = min(mce),
                     max_mce = max(mce),
                     mean_fp = mean(fp),
                     mean_mce = mean(mce),
                     stdev_fp = sd(fp),
                     stdev_mce = sd(mce)) %>%
    dplyr::mutate(range_fp = max_fp - min_fp,
                  range_mce = max_mce - min_mce) %>%
    knitr::kable()
```