---
title: "Lab to field model"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
---

```{r global_options, include=FALSE}
  knitr::opts_chunk$set(fig.path='figures/', warning=FALSE, message=FALSE, cache=FALSE)
```

```{r load_libraries, echo=FALSE}
  library(tidyverse)
  library(lme4)
  library(plyr)
  library(MASS)
```

# Load files

* data

```{r load_data, echo=FALSE}
  lab_grav <- readRDS("../r_files/lab_grav_merged.RDS")
  field_emissions <- readRDS("../r_files/field_emissions.RDS")
```

* functions

```{r load_functions, echo=FALSE}
  source("../r_scripts/models.R")
  source("../r_scripts/functions.R")
```

* metadata

```{r load_meta, echo=FALSE}
  lab_samples <- readRDS("../r_files/lab_meta.RDS")
  field_samples <- readRDS("../r_files/field_meta.RDS")
```

# Tidy data

## Lab data

* remove start up and shutdown
* select only wood tests
* filter out Okote tests
* create general stove categories

```{r, echo=FALSE}
  lab_data <- lab_grav %>%
              dplyr::select(-units) %>%
              tidyr::spread(var, val) %>% 
              dplyr::select(id, sample_id, pm_ef, bc_ef, pm_mass, bc_mass,
                            pm_rate, bc_rate, fp, mce) %>%
              tidyr::gather("pol", "val", 3:8) %>%
              dplyr::left_join(lab_samples, by = "id") %>%
              dplyr::filter(sample_id != "start_up", sample_id != "shutdown") %>% 
              dplyr::filter(fuel != "Okote") %>%
              dplyr::filter(!grepl("mass", pol)) %>%
              dplyr::filter(fuel_type == "wood") %>%
              dplyr::filter(!is.na(val), !is.na(fp), !is.na(mce)) %>%
              dplyr::mutate(stove_cat = "traditional open fire",
                            stove_cat = ifelse(grepl("Rocket", stove),
                                               "rocket elbow", stove_cat),
                            stove_cat = ifelse(grepl("Sunken|Justa", stove),
                                               "built-in", stove_cat))
```

## Field data

* create general stove categories

```{r, echo=FALSE}
  field_data <- field_emissions %>%
                dplyr::filter(grepl("pm|bc|firepower|mce", var)) %>%
                dplyr::select(-units, - pol) %>%
                tidyr::spread(var, val) %>%
                dplyr::select(hh_id, pm_ef, bc_ef, pm_mass, bc_mass,
                              pm_rate, bc_rate, firepower, mce) %>%
                dplyr::rename(fp = firepower) %>%
                tidyr::gather("pol", "val", 2:7) %>%
                dplyr::filter(!grepl("mass", pol)) %>%
                dplyr::left_join(dplyr::select(field_samples, hh_id,
                                               stove_type, fuel_type), by = "hh_id") %>%
                dplyr::filter(!is.na(val), !is.na(fp), !is.na(mce)) %>%
                dplyr::mutate(stove_cat = "traditional open fire",
                              stove_cat = ifelse(grepl("Rocket", stove_type),
                                                 "rocket elbow", stove_cat))
```

# Develop models using lab data

## Firepower models (with diagnostics)

```{r}
  f <- c("val ~ fp")
```

```{r, fig.height=6, fig.width=6, echo=FALSE, results='hide', fig.keep='all'}
  lapply(f, function(x) plot_simple_lm(data = lab_data, eqn = x))
```

## Firepower model summary table

```{r}
  knitr::kable(model_list)
```

## Firepower model conclusions
* Best linear fits: black carbon rate, 

## MCE models

```{r}
    f <- c("val ~ mce")
```

```{r, fig.height=6, fig.width=6, echo=FALSE, results='hide', fig.keep='all'}
  lapply(f, function(x) plot_simple_lm(data = lab_data, eqn = x))
```

# Predict field data using lab data

* no boxcox transform implemented yet

```{r, echo=FALSE}
    f <- c("val ~ fp", "val ~ poly(fp, 2)", "val ~ mce", "val ~ fp + mce + fp*mce")
    pols <- c("pm_ef", "pm_rate", "bc_ef", "bc_rate")
```

```{r, echo=FALSE}
  predict_field_data <- lapply(f, function(y) lapply(pols, function(x)
                             predict_boxcox_model(train_data = lab_data, test_data = field_data,
                                                  eqn = y, pollutant = x,
                                                  stove_category = "rocket elbow")) %>%
                               bind_rows()) %>%
                               bind_rows() 
```

```{r, echo=FALSE}
  predict_field_data2 <- lapply(f, function(y) lapply(pols, function(x)
                             predict_boxcox_model(train_data = lab_data, test_data = field_data,
                                                  eqn = y, pollutant = x,
                                                  stove_category = "traditional open fire")) %>%
                               bind_rows()) %>%
                               bind_rows() 
```

```{r, echo=FALSE}
  predict_field <- bind_rows(predict_field_data, predict_field_data2)
```

```{r, echo=FALSE, fig.height=15, fig.width=15, fig.keep="none"}
  ggplot(predict_field, aes(x = val, y = pred_val, color = hh_id)) +
    geom_point(size = 3) +
    facet_wrap(pol~equation, ncol = 4, scales = "free") + 
    theme_bw() +
    geom_abline(slope = 1, intercept = 0) + 
    xlab("measured value") + 
    ylab("predicted value") + 
    theme(text = element_text(size = 16))
    
```

