---
title: "Lab grav"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
---

```{r global_options, include=FALSE}
  knitr::opts_chunk$set(fig.path='figures/', warning=FALSE, message=FALSE, cache=FALSE)
```

```{r load_libraries}
  library(tidyverse)
  library(forcats)
  library(gridExtra)
```

# Load files

* data

```{r load_data}
  grav <- readRDS("../r_files/lab_grav.RDS")
```

* functions

```{r load_functions}
  source("../r_scripts/plots.R")
```

* metadata

```{r load_meta}
  samples <- readRDS("../r_files/lab_meta.RDS")
```

# Organize

* tidy data

```{r tidy_data}
  grav <- grav %>%
          dplyr::mutate(dur = (end_time - start_time) * (86400 / 60)) %>%
          dplyr::select(-start_time , -end_time) %>%
          dplyr::mutate(sample_id = gsub("Start Up|Start up", "start_up", sample_id),
                        sample_id = gsub("Shut Down", "shut_down", sample_id),
                        sample_id = gsub(" [:(:][0-9])|^2nd |/Restart", "", sample_id),
                        sample_id = gsub("Sample 2|Sample 2 [:(:]2nd try[:):]", "fp_1", sample_id),
                        sample_id = gsub("Sample 3", "fp_2", sample_id),
                        sample_id = gsub("Sample 4|Relight|Restart", "fp_3", sample_id),
                        sample_id = gsub("Sample 5|Sample5", "fp_4", sample_id),
                        sample_id = gsub("Sample 6", "fp_5", sample_id),
                        sample_id = gsub("Sample 7", "fp_6", sample_id),
                        sample_id = gsub("Sample 8", "fp_7", sample_id),
                        sample_id = as.factor(sample_id)) 

  # fix typos
  fp4 <- c(156, 184, 198, 226, 240, 247, 268, 275)
  fp5 <- c(157, 185, 199, 227, 241, 248, 269, 276)
  grav$sample_id[fp4] <- "fp_4" 
  grav$sample_id[fp5] <- "fp_5"
```

* add stove fuel information 

```{r add_test_info}
  grav <- grav %>%
          dplyr::left_join(samples, by = "id")
```

# Data visualization

```{r plot_pm, fig.height=30, fig.width=12, echo=FALSE}
  p_grav <- grav %>%
            dplyr::group_by(stove, fuel, sample_id) %>%
            dplyr::summarise(pm_ef = mean(pm_ef, na.rm = TRUE))

 ggplot(p_grav, aes_string(x = "sample_id", y = "pm_ef", fill = "fuel")) +
  geom_col(position = "dodge") +
  theme_bw() + 
  facet_wrap(~stove, scales = "free", ncol = 1)
  ylab("pm2.5 ef (g/kg fuel)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "top")
```


# Firepower vs. PM EF

* three stone fire (linear model)

```{r, echo=TRUE, warning=FALSE, message=FALSE, results='markup', cache=FALSE}
  # m_grav <- dplyr::filter(grav, stove == "Three stone fire") %>%
  #           dplyr::mutate(fp_2 = fp*fp)
  # model <- lm(pm_ef ~ fp, data = m_grav)
  # c <- coefficients(model)
  # summary(model)

```

* three stone fire (quadratic model)

```{r, echo=TRUE, warning=FALSE, message=FALSE, results='markup', cache=FALSE}
  # model <- lm(pm_ef ~ fp + fp_2, data = m_grav)
  # c <- coefficients(model)
  # summary(model)

```

```{r, fig.width=12, fig.height=10, echo=FALSE}
 # p1 <- ggplot(m_grav, aes(x = fp, y = pm_ef)) +
 #    geom_point() +
 #    geom_smooth(method = "lm") +
 #    theme_bw() +
 #    xlab("firepower (kW)") + 
 #    ylab("pm ef (g/kg fuel)") + 
 #    theme(axis.text.x = element_text(size = 20)) +
 #    theme(axis.text.y = element_text(size = 20),
 #          axis.title=element_text(size=20))
 # 
 # p2 <- ggplot(m_grav, aes(x = fp, y = pm_ef, colour = fuel)) +
 #    geom_point() +
 #    geom_smooth(method = "lm") +
 #    theme_bw() +
 #    xlab("firepower (kW)") + 
 #    ylab("pm ef (g/kg fuel)") + 
 #    theme(axis.text.x = element_text(size = 20)) +
 #    theme(axis.text.y = element_text(size = 20),
 #          axis.title=element_text(size=20))
 # 
 #   grid.arrange(p1, p2, ncol = 2)
```

* clay ring (linear model)

```{r, echo=TRUE, warning=FALSE, message=FALSE, results='markup', cache=FALSE}
  # m_grav <- dplyr::filter(grav, stove == "Clay ring") %>%
  #           dplyr::mutate(fp_2 = fp*fp)
  # model <- lm(pm_ef ~ fp, data = m_grav)
  # c <- coefficients(model)
  # summary(model)

```

* clay ring (quadratic model)

```{r, echo=TRUE, warning=FALSE, message=FALSE, results='markup', cache=FALSE}
  # model <- lm(pm_ef ~ fp + fp_2, data = m_grav)
  # c <- coefficients(model)
  # summary(model)

```

```{r, fig.width=12, fig.height=10, echo=FALSE}
 # p1 <- ggplot(m_grav, aes(x = fp, y = pm_ef)) +
 #    geom_point() +
 #    geom_smooth(method = "lm") +
 #    theme_bw() +
 #    xlab("firepower (kW)") + 
 #    ylab("pm ef (g/kg fuel)") + 
 #    theme(axis.text.x = element_text(size = 20)) +
 #    theme(axis.text.y = element_text(size = 20),
 #          axis.title=element_text(size=20))
 # 
 # p2 <- ggplot(m_grav, aes(x = fp, y = pm_ef, colour = fuel)) +
 #    geom_point() +
 #    geom_smooth(method = "lm") +
 #    theme_bw() +
 #    xlab("firepower (kW)") + 
 #    ylab("pm ef (g/kg fuel)") + 
 #    theme(axis.text.x = element_text(size = 20)) +
 #    theme(axis.text.y = element_text(size = 20),
 #          axis.title=element_text(size=20))
 # 
 #   grid.arrange(p1, p2, ncol = 2)
```

* rocket elbow (linear model)

```{r, echo=TRUE, warning=FALSE, message=FALSE, results='markup', cache=FALSE}
  # m_grav <- dplyr::filter(grav, stove == "Rocket elbow") %>%
  #           dplyr::mutate(fp_2 = fp*fp)
  # model <- lm(pm_ef ~ fp, data = m_grav)
  # c <- coefficients(model)
  # summary(model)

```

* rocket elbow (quadratic model)

```{r, echo=TRUE, warning=FALSE, message=FALSE, results='markup', cache=FALSE}
  # model <- lm(pm_ef ~ fp + fp_2, data = m_grav)
  # c <- coefficients(model)
  # summary(model)

```

```{r, fig.width=12, fig.height=10, echo=FALSE}
 # p1 <- ggplot(m_grav, aes(x = fp, y = pm_ef)) +
 #    geom_point() +
 #    geom_smooth(method = "lm") +
 #    theme_bw() +
 #    xlab("firepower (kW)") + 
 #    ylab("pm ef (g/kg fuel)") + 
 #    theme(axis.text.x = element_text(size = 20)) +
 #    theme(axis.text.y = element_text(size = 20),
 #          axis.title=element_text(size=20))
 # 
 # p2 <- ggplot(m_grav, aes(x = fp, y = pm_ef, colour = fuel)) +
 #    geom_point() +
 #    geom_smooth(method = "lm") +
 #    theme_bw() +
 #    xlab("firepower (kW)") + 
 #    ylab("pm ef (g/kg fuel)") + 
 #    theme(axis.text.x = element_text(size = 20)) +
 #    theme(axis.text.y = element_text(size = 20),
 #          axis.title=element_text(size=20))
 # 
 #   grid.arrange(p1, p2, ncol = 2)
```

# MCE vs. PM EF

```{r plot_pm_mce, fig.width=12, fig.height=10, echo=FALSE}
  #ggplot(grav, aes(x = mce, y = pm_ef, colour = stove)) +
    #geom_point() +
    #facet_wrap(stove~fuel, scales = "free") +
    #geom_smooth(method = "lm") +
    #xlab("mce") + 
    #ylab("pm ef (g/kg fuel)") + 
    #theme(axis.text.x = element_text(size = 20)) +
    #theme(axis.text.y = element_text(size = 20),
          #axis.title=element_text(size=20))
    