---
title: "Build lab model"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
---

```{r load_libraries, echo=FALSE, message=FALSE}
  library(mfp)      # transformation analysis
  #library(glmulti)  # interaction analysis
  library(tidyverse)
  library(knitr)
  library(MASS)      # boxcox transform
  library(lmtest)    # bptest
  library(lme4)
  library(effects)
  library(leaps)
  library(rms) 
  library(arm)
  library(gvlma)
```

```{r global_options, include=FALSE}
  knitr::opts_chunk$set(fig.path='figures/', warning=FALSE, message=FALSE, cache=FALSE)
```

# Organize lab data

## Load files

* data

```{r load_data}
  lab_grav <- readRDS("../r_files/lab_grav_merged.RDS")
```

* functions

```{r load_functions}
  source("../r_scripts/lab_model_metrics.R")
  source("../r_scripts/functions.R")
```

* metadata

```{r load_meta}
  lab_samples <- readRDS("../r_files/lab_meta.RDS")
```

## Tidy data

* select bc emissions rate as outcome
* merge with metadata
* select only wood tests
* filter out Okote tests

```{r}
  lab_data <- lab_grav %>%
              dplyr::select(-units) %>%
              tidyr::spread(var, val) %>% 
              dplyr::select(id, sample_id, bc_rate, fp, mce) %>%
              dplyr::left_join(lab_samples, by = "id") %>%
              dplyr::filter(fuel != "Okote") %>%
              dplyr::filter(fuel_type == "wood") %>%
              dplyr::filter(!is.na(bc_rate), !is.na(fp), !is.na(mce))
```

# Basic model: firepower

## Model setup

* start by setting up a model that regresses firpower, mce, and their interaction to bc emissions rate for all lab data

```{r basic_fp, results='hide'}
# Build basic linear firepower model
  eqn <- formula(bc_rate ~ fp)
  basic_model <- lm(eqn, data = lab_data)
  basic_coef <- coef(basic_model)
  rmse <- rmse_id_avg(basic_model, lab_data)
  basic_rmse <- mean(rmse$rmse)
```

## Plot model

```{r, echo=FALSE}
  ggplot(lab_data, aes(x = fp, y = bc_rate, color = stove)) +
    geom_point(size = 2) +
          theme_bw() + 
          geom_smooth(method = "lm", formula = 'y ~ x',
                      color = 'black') + 
    ylab("bc emissions rate (mg/min)") + 
    xlab("firepower (kW)")
```

## Diagnostic plots

```{r, echo=FALSE}
  par(mfrow = c(2, 2))
  plot(basic_model)
```

## Summary

The resulting linear model is: $$\text{BC rate} = `r round(basic_coef[2], digits = 3)` \times FP + `r round(basic_coef[1], digits = 3)`$$ with a *rmse* of `r round(basic_rmse, digits = 3)` mg/min.

```{r, echo=FALSE}
  summary(basic_model)
```

* none of the coefficients have significant p-values, although the model itself has a significant p-value
* residual vs. fitted plot to show that the data may have some non-linear patterns
* normal q-q plot shows that the residuals may not be normally distributed
* scale-location plot indicates that the residuals are not spread equally along the range of predictors therefore this model may fail homoscedasticity
* residuals vs. leverage plot indicates there may be some influential outliers

## Is heteroscedasticity an issue?
```{r}
  # basic model
  eqn <- formula(bc_rate ~ fp)
  basic_model <- lm(eqn, data = lab_data)
  bp_test <- lmtest::bptest(basic_model)

# remove start up and shutdown data
  eqn <- formula(bc_rate ~ fp)
  lab_data_noss <- lab_data %>%
                   dplyr::filter(sample_id != "start_up",
                                 sample_id != "shutdown")
  basic_model <- lm(eqn, data = lab_data_noss)
  bp_test_noss <- lmtest::bptest(basic_model)

# try square root transform
  eqn <- formula(bc_rate ~ I(fp^2))
  basic_model <- lm(eqn, data = lab_data)
  bp_test_sq <- lmtest::bptest(basic_model)
```

Basic model shows signs of heteroscedasticity (p = `r round(bp_test[[4]], 6)`). Removing the start up and shutdown data improves the model (p = `r round(bp_test_noss[[4]], 6)`). A square transform (see *mfp* below) helps as well (p = `r round(bp_test_sq[[4]], 6)`). 

## Is the model improved with a box-cox transform?

* run box-cox transform without start up and shutdown data

```{r}
  # calculate lambda
  basic_model <- lm(bc_rate ~ fp, data = lab_data_noss)
  box_cox <- boxcox(basic_model, plotit = FALSE)
  lambda <- box_cox$x[which.max(box_cox$y)]
  
  # run transformed model
  lab_data_bc <- dplyr::mutate(lab_data_noss, bc_rate_trans = bc_rate^lambda)
  basic_model_bc <- lm(bc_rate_trans ~ fp, data = lab_data_bc)

  # calculate coefficients and rmse
  basic_bc_coef <- coef(basic_model_bc)
  rmse_bc <- rmse_id_avg(basic_model_bc, lab_data_bc)
  basic_rmse_bc <- mean(rmse_bc$rmse)
```

Plot transformed data

```{r, echo=FALSE}
  ggplot(lab_data_bc, aes(x = fp, y = bc_rate_trans, color = stove)) +
    geom_point(size = 2) +
          theme_bw() + 
          geom_smooth(method = "lm", formula = 'y ~ x',
                      color = 'black') + 
    ylab("bc emissions rate (transformed)") + 
    xlab("firepower (kW)")
```

Diagnostic plots

```{r, echo=FALSE}
  par(mfrow = c(2, 2))
  plot(basic_model_bc)
```

Box-cox model summary

The resulting linear model is: $$\text{BC rate}^\lambda = `r round(basic_bc_coef[2], digits = 3)` \times FP + `r round(basic_bc_coef[1], digits = 3)`$$  with a *rmse* of `r round(basic_rmse_bc, digits = 3)` in transformed units.

```{r, echo=FALSE}
  summary(basic_model)
```

# Basic model: stove-type and fuel-type as a predictors

If the stove of fuel variables can explain some of the emissions variability in the firepower vs. bc emissions rate relationship, its likely that adding stove type and fuel type as predictors will explain more of the variance in bc emissions rate than firepower alone. 

## Build model

```{r}
sf_model <-  lm(bc_rate_trans ~ fp + stove + fuel, data = lab_data_bc)
```

## Diagnostic plots

```{r, echo=FALSE}
  par(mfrow = c(2, 2))
  plot(sf_model)
```

## Summary

```{r}
summary(sf_model)
```

The resulting linear model has a *rmse* of `r round(calc_rmse(sf_model), digits = 3)` in transformed units and an *adjusted R squared* of `r round(summary(sf_model)$adj.r.square, digits = 3)`.

## Does the model improve with MCE?

Build model

```{r}
sf_mce_model <-  lm(bc_rate_trans ~ fp + stove + fuel + mce, data = lab_data_bc)
```

Diagnostic plots

```{r, echo=FALSE}
  par(mfrow = c(2, 2))
  plot(sf_mce_model)
```

Summary

```{r}
summary(sf_mce_model)
```

The resulting linear model has a *rmse* of `r round(calc_rmse(sf_model), digits = 3)` in transformed units and an *adjusted R squared* of `r round(summary(sf_model)$adj.r.square, digits = 3)`.

# Variable correlation

Quick look how the correlation between firepower and mce

```{r}
# plot pairs
  data <- subset(lab_data_bc, select = c(bc_rate_trans, fp, mce))
  pairs(data)
```

# Mfp analysis (variable selection, transformation and scaling)

The *mfp* package is used for variable selection, transformation and scaling.

```{r}
  # full equation
  eqn <- formula(bc_rate_trans ~ stove + fuel + fp(fp) + fp(mce)) 

  # run mfp
  mfp_model <- mfp(eqn, data = lab_data_bc, select = 0.05)

  # fit suggested model
  test_mfp <- lm(mfp_model$formula, data = lab_data_bc)
```

Diagnostic plots

```{r, echo=FALSE}
  par(mfrow = c(2, 2))
  plot(test_mfp)
```

Summary

The mfp model results in the following formula: `r mfp_model$formula`

```{r}
summary(test_mfp)
```

The resulting linear model has a *rmse* of `r round(calc_rmse(sf_model), digits = 3)` in transformed units and an *adjusted R squared* of `r round(summary(sf_model)$adj.r.square, digits = 3)`.

Check to see if the suggested scaling has been applied correctly

```{r}
  # create a transformed and re-scaled dataframe 
  lab_data_trans <- transform(lab_data_bc)

# check mfp has worked i.e. no transformations / scaling required on transformed data set
  eqn <- formula(bc_rate_trans ~ stove + fuel + fp(fp_nsqrt) + fp(fp_log)) 
  mfp_model <- mfp(eqn, data = lab_data_trans, select = 0.05)
```

Same as above? - no

```{r}
  summary(mfp_model)
```

## Mfp - bootstrap

```{r, echo=TRUE, message=FALSE, warning=FALSE, tidy=TRUE, results='markup', cache=TRUE}
 # full equation
  eqn <- formula(ve_oxy ~ sex + fp(hr_oxy) + fp(age) + fp(chest) + fp(height) +
                fp(hip) + fp(hr_rest_oxy) + fp(waist) + fp(weight)) 
 # run mfp 10,000 times, sampling from list of participants
  boot_data <- mfp_bootstrap_f(group_1_data, eqn, 10000)
```

# glmulti analysis (variable selection and 2-way interactions within multi-level model) 