---
title: "Build lab model"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
---

```{r load_libraries, echo=FALSE, message=FALSE}
  library(mfp)      # transformation analysis
  #library(glmulti)  # interaction analysis
  library(tidyverse)
  library(knitr)
  library(MASS)      # boxcox transform
  library(lmtest)    # bptest
  library(lme4)
  library(effects)
  library(leaps)
  library(rms) 
  library(arm)
  library(gvlma)
```

```{r global_options, include=FALSE}
  knitr::opts_chunk$set(fig.path='figures/', warning=FALSE, message=FALSE, cache=FALSE)
```

# Organize lab data

## Load files

* data

```{r load_data}
  lab_grav <- readRDS("../r_files/lab_grav_merged.RDS")
```

* functions

```{r load_functions}
  source("../r_scripts/lab_model_metrics.R")
  source("../r_scripts/functions.R")
```

* metadata

```{r load_meta}
  lab_samples <- readRDS("../r_files/lab_meta.RDS")
```

## Tidy data

* select bc emissions rate as outcome
* merge with metadata
* select only wood tests
* filter out Okote tests

```{r}
  lab_data <- lab_grav %>%
              dplyr::select(-units) %>%
              tidyr::spread(var, val) %>% 
              dplyr::select(id, sample_id, bc_ef, fp, mce) %>%
              dplyr::left_join(lab_samples, by = "id") %>%
              dplyr::filter(fuel != "Okote") %>%
              dplyr::filter(fuel_type == "wood") %>%
              dplyr::filter(!is.na(bc_ef), !is.na(fp), !is.na(mce))
```

# Basic model: firepower

*The goal of the basic model is to examine whether firepower is a meaningful predictor of emissions*

## Model setup

The basic model uses only firepower as a predictor for black carbon emissions rate. 

```{r basic_fp, results='hide'}
  # Build basic linear firepower model
  eqn <- formula(bc_ef ~ fp)
  basic_model <- lm(eqn, data = lab_data)
  basic_coef <- coef(basic_model)

  basic_rmse <- calc_rmse(basic_model)
```

## Plot model

```{r, echo=FALSE}
  ggplot(lab_data, aes(x = fp, y = bc_ef, color = stove)) +
    geom_point(size = 2) +
          theme_bw() + 
          geom_smooth(method = "lm", formula = 'y ~ x',
                      color = 'black') + 
    ylab("bc emissions rate (mg/min)") + 
    xlab("firepower (kW)")
```

## Diagnostic plots

```{r, echo=FALSE}
  par(mfrow = c(2, 2))
  plot(basic_model)
```

## Basic model summary

The resulting linear model is: $$\text{BC rate} = `r round(basic_coef[2], digits = 3)` \times FP + `r round(basic_coef[1], digits = 3)`$$ with a *rmse* of `r round(basic_rmse, digits = 3)` mg/min.

Firepower is a significant predictor; however, the variance explained by the model is small.

```{r, echo=FALSE}
  summary(basic_model)
```

## Does removing start up and shutdown data improve the model?

```{r}
# remove start up and shutdown data
  eqn <- formula(bc_ef ~ fp)
  lab_data_noss <- lab_data %>%
                   dplyr::filter(sample_id != "start_up",
                                 sample_id != "shutdown")
  basic_model <- lm(eqn, data = lab_data_noss)
  
  basic_rmse <- calc_rmse(basic_model)
```

Summary

The resulting linear model has a *rmse* of `r round(basic_rmse, digits = 3)` mg/min.

Removing start up and shutdown data does not improve the model.

```{r, echo=FALSE}
  summary(basic_model)
```

## Is the model improved with a box-cox transform?

```{r}
  # calculate lambda
  basic_model <- lm(bc_ef ~ fp, data = lab_data)
  box_cox <- boxcox(basic_model, plotit = FALSE)
  lambda <- box_cox$x[which.max(box_cox$y)]
```

The box-cox transform gives $$\lambda = `r lambda[1]`$$.

```{r}
  # run transformed model
  lab_data_bc <- dplyr::mutate(lab_data, bc_ef_trans = bc_ef^lambda)
  basic_model_bc <- lm(bc_ef_trans ~ fp, data = lab_data_bc)
```

```{r}
  # calculate rmse by transforming residuals then calculating rmse
  basic_rmse_bc <- calc_rmse_bc(basic_model_bc)
```

Plot transformed data

```{r, echo=FALSE}
  ggplot(lab_data_bc, aes(x = fp, y = bc_ef_trans, color = stove)) +
    geom_point(size = 2) +
          theme_bw() + 
          geom_smooth(method = "lm", formula = 'y ~ x',
                      color = 'black') + 
    ylab("bc emissions rate (transformed)") + 
    xlab("firepower (kW)")
```

Diagnostic plots

```{r, echo=FALSE}
  par(mfrow = c(2, 2))
  plot(basic_model_bc)
```

Summary

The resulting linear model has a *rmse* of `r basic_rmse_bc` in mg/min. 

The boxcox transform model does signficantly better in terms of rmse and slightly better in terms of variance explained (Note: the model summary is in transformed units).

```{r, echo=FALSE}
  summary(basic_model_bc)
```

## Does mfp analysis improve the firepower model?

The *mfp* package is used for variable selection, transformation and scaling.

```{r}
  # full equation
  eqn <- formula(bc_ef ~ fp(fp))

  # run mfp
  mfp_model <- mfp(eqn, data = lab_data, select = 0.05)

  # fit suggested model
  test_mfp <- lm(mfp_model$formula, data = lab_data)
  basic_rmse <- calc_rmse(test_mfp)
```

Summary

The resulting mfp model has a *rmse* of `r basic_rmse` in mg/min. The only variable selected was firepower to the first power.

```{r, echo=FALSE}
  summary(test_mfp)
```

## Does adding stove type and fuel type as predictors change the mfp model?

```{r}
  # full equation
  eqn <- formula(bc_ef ~ fp(fp) + stove + fuel)

  # run mfp
  mfp_model <- mfp(eqn, data = lab_data, select = 0.05)

  # fit suggested model
  test_mfp <- lm(mfp_model$formula, data = lab_data)
  basic_rmse <- calc_rmse(test_mfp)
```

Summary

The resulting mfp model has a *rmse* of `r basic_rmse` in mg/min. 

The firepower variable is only selected to the first power again and the rmse doesn't change much.

```{r, echo=FALSE}
  summary(test_mfp)
```

## What happens when we bootstrap the data?

```{r}
 # full equation
  eqn <- formula(bc_ef ~ stove + fuel + fp(fp))
 # run mfp 100 times, sampling from list of stove/fuel tests
  boot_data <- mfp_bootstrap(lab_data_bc, eqn, 500)
```

```{r, echo=FALSE}
  out <- data.frame(var = integer(9), pct = numeric(9))

  num <- nrow(subset(boot_data, names == "fp" & power1 != "."))
  total <- nrow(subset(boot_data, names == "fp"))
  out$pct[1] <- num*100/total
  out$var[1] <- "fp"

  num <- nrow(subset(boot_data, names == "stoveJusta (Artisan)" & power1 != "."))
  total <- nrow(subset(boot_data, names == "stoveJusta (Artisan)"))
  out$pct[2] <- num*100/total
  out$var[2] <- "stoveJusta (Artisan)"

  num <- nrow(subset(boot_data, names == "stoveJusta (HM5000)" & power1 != "."))
  total <- nrow(subset(boot_data, names == "stoveJusta (HM5000)"))
  out$pct[3] <- num*100/total
  out$var[3] <- "stoveJusta (HM5000)"

  num <- nrow(subset(boot_data, names == "stoveRocket Elbow (Chulika)" & power1 != "."))
  total <- nrow(subset(boot_data, names == "stoveRocket Elbow (Chulika)"))
  out$pct[4] <- num*100/total
  out$var[4] <- "stoveRocket Elbow (Chulika)"

  num <- nrow(subset(boot_data, names == "stoveRocket Elbow (G3300)" & power1 != "."))
  total <- nrow(subset(boot_data, names == "stoveRocket Elbow (G3300)"))
  out$pct[5] <- num*100/total
  out$var[5] <- "stoveRocket Elbow (G3300)"

  num <- nrow(subset(boot_data, names == "stoveSunken Pot" & power1 != "."))
  total <- nrow(subset(boot_data, names == "stoveSunken Pot"))
  out$pct[6] <- num*100/total
  out$var[6] <- "stoveSunken Pot"

  num <- nrow(subset(boot_data, names == "stoveThree Stone Fire" & power1 != "."))
  total <- nrow(subset(boot_data, names == "stoveThree Stone Fire"))
  out$pct[7] <- num*100/total
  out$var[7] <- "stoveThree Stone Fire"

  num <- nrow(subset(boot_data, names == "stoveVikram" & power1 != "."))
  total <- nrow(subset(boot_data, names == "stoveVikram"))
  out$pct[8] <- num*100/total
  out$var[8] <- "stoveVikram"

  num <- nrow(subset(boot_data, names == "fuelEucalyptus" & power1 != "."))
  total <- nrow(subset(boot_data, names == "fuelEucalyptus"))
  out$pct[9] <- num*100/total
  out$var[9] <- "fuelEucalyptus"

  num <- subset(boot_data, (names == "fp" | names == "mce" | names == "stoveJusta (Artisan)" |
                              names == "stoveJusta (HM5000)" | names == "stoveRocket Elbow (Chulika)" |
                              names == "stoveRocket Elbow (G3300)" | names == "stoveSunken Pot" |
                              names == "stoveThree Stone Fire" | names == "stoveVikram" |
                              names == "fuelEucalyptus") & power1 != ".")

  # round
  out$pct <- round(out$pct,1)
  var_freq <- out
```

Summary

The table gives the percent of the time each variable appears in any form.

The mfp/bootstrapping method chooses firepower as an important variable 100% of the time. 

```{r}
  kable(var_freq)
```

# Secondary model: firepower and mce

*The goal of this model is to examine how mce compares to firepower as a predictor of emissions*

## Variable correlation

How does firepower correlate wtih mce?

```{r, echo=FALSE}
  # plot pairs
  data <- subset(lab_data, select = c(bc_ef, fp, mce))
  pairs(data)
```

## Model setup

The secondary model uses firepower, mce and their interaction term as a predictor for black carbon emissions rate. 

```{r, results='hide'}
  # Build basic linear firepower model
  eqn <- formula(bc_ef ~ fp + mce + fp*mce)
  basic_model <- lm(eqn, data = lab_data)
  basic_coef <- coef(basic_model)
  #rmse <- rmse_id_avg(basic_model, lab_data, lab_data$bc_ef)
  basic_rmse <- calc_rmse(basic_model)
```

## Diagnostic plots

```{r, echo=FALSE}
  par(mfrow = c(2, 2))
  plot(basic_model)
```

## Secondary model summary

The resulting linear model has a *rmse* of `r round(basic_rmse, digits = 3)` mg/min.

There is little change from the baseline firepower model when mce is added. 

```{r, echo=FALSE}
  summary(basic_model)
```

## How does mce do on its own?

```{r, results='hide'}
  # Build basic linear firepower model
  eqn <- formula(bc_ef ~ mce)
  basic_model <- lm(eqn, data = lab_data)
  basic_coef <- coef(basic_model)
  #rmse <- rmse_id_avg(basic_model, lab_data, lab_data$bc_ef)
  basic_rmse <- calc_rmse(basic_model)
```

Plot model

```{r, echo=FALSE}
  ggplot(lab_data, aes(x = mce, y = bc_ef, color = stove)) +
    geom_point(size = 2) +
          theme_bw() + 
          geom_smooth(method = "lm", formula = 'y ~ x',
                      color = 'black') + 
    ylab("bc emissions rate (mg/min)") + 
    xlab("mce")
```

Diagnostic plots

```{r, echo=FALSE}
  par(mfrow = c(2, 2))
  plot(basic_model)
```

Summary

When mce is the only predictor the resulting linear model has a *rmse* of `r round(basic_rmse, digits = 3)` mg/min. And the percent variance explained is very low. 

```{r, echo=FALSE}
  summary(basic_model)
```

## Does a boxcox model improve the mce only model?

```{r}
  # calculate lambda
  basic_model <- lm(bc_ef ~ mce, data = lab_data)
  box_cox <- boxcox(basic_model, plotit = FALSE)
  lambda <- box_cox$x[which.max(box_cox$y)]
```

The box-cox transform gives $$\lambda = `r lambda[1]`$$.

```{r}
  # run transformed model
  lab_data_bc <- dplyr::mutate(lab_data, bc_ef_trans = bc_ef^lambda)
  basic_model_bc <- lm(bc_ef_trans ~ mce, data = lab_data_bc)
```

```{r}
  # calculate rmse by transforming residuals then calculating rmse
  basic_rmse_bc <- calc_rmse_bc(basic_model_bc)
```

Plot transformed data

```{r, echo=FALSE}
  ggplot(lab_data_bc, aes(x = mce, y = bc_ef_trans, color = stove)) +
    geom_point(size = 2) +
          theme_bw() + 
          geom_smooth(method = "lm", formula = 'y ~ x',
                      color = 'black') + 
    ylab("bc emissions rate (transformed)") + 
    xlab("firepower (kW)")
```

Diagnostic plots

```{r, echo=FALSE}
  par(mfrow = c(2, 2))
  plot(basic_model_bc)
```

Summary

The resulting linear model has a *rmse* of `r basic_rmse_bc` in mg/min. 

The boxcox transform model does signficantly better in terms of rmse and slightly better in terms of variance explained (Note: the model summary is in transformed units).

```{r, echo=FALSE}
  summary(basic_model_bc)
```

## Does mfp analysis improve the mce only model?

```{r}
  # full equation
  eqn <- formula(bc_ef ~ fp(mce))

  # run mfp
  mfp_model <- mfp(eqn, data = lab_data, select = 0.05)

  # fit suggested model
  test_mfp <- lm(mfp_model$formula, data = lab_data)
  basic_rmse <- calc_rmse(test_mfp)
```

Summary

The resulting mfp model has a *rmse* of `r basic_rmse` in mg/min. Although, mce is not selected as a significant variable. 

```{r, echo=FALSE}
  summary(test_mfp)
```

## Does mfp analysis improve when both firepower and mce are in the model?

The *mfp* package is used for variable selection, transformation and scaling.

```{r}
  # full equation
  eqn <- formula(bc_ef ~ fp(fp) + fp(mce))

  # run mfp
  mfp_model <- mfp(eqn, data = lab_data, select = 0.05)

  # fit suggested model
  test_mfp <- lm(mfp_model$formula, data = lab_data)
  basic_rmse <- calc_rmse(test_mfp)
```

Summary

The resulting mfp model has a *rmse* of `r basic_rmse` in mg/min. 

```{r, echo=FALSE}
  summary(test_mfp)
```

## Does adding stove type and fuel type as predictors change the mfp model (when both fp and mce are included)?

```{r}
  # full equation
  eqn <- formula(bc_ef ~ fp(fp) + fp(mce) + stove + fuel)

  # run mfp
  mfp_model <- mfp(eqn, data = lab_data, select = 0.05)

  # fit suggested model
  test_mfp <- lm(mfp_model$formula, data = lab_data)
  basic_rmse <- calc_rmse(test_mfp)
```

Summary

The resulting mfp model has a *rmse* of `r basic_rmse` in mg/min. Firepower is chosen to the first power and mce is not chosen as an important variable.

```{r, echo=FALSE}
  summary(test_mfp)
```

## What happens when we bootstrap the data?

```{r}
 # full equation
  eqn <- formula(bc_ef ~ stove + fuel + fp(fp) + fp(mce))
 # run mfp 100 times, sampling from list of stove/fuel tests
  boot_data <- mfp_bootstrap(lab_data_bc, eqn, 500)
```

```{r, echo=FALSE}
  out <- data.frame(var = integer(10), pct = numeric(10))

  num <- nrow(subset(boot_data, names == "fp" & power1 != "."))
  total <- nrow(subset(boot_data, names == "fp"))
  out$pct[1] <- num*100/total
  out$var[1] <- "fp"

  num <- nrow(subset(boot_data, names == "mce" & power1 != "."))
  total <- nrow(subset(boot_data, names == "mce"))
  out$pct[2] <- num*100/total
  out$var[2] <- "mce"

  num <- nrow(subset(boot_data, names == "stoveJusta (Artisan)" & power1 != "."))
  total <- nrow(subset(boot_data, names == "stoveJusta (Artisan)"))
  out$pct[3] <- num*100/total
  out$var[3] <- "stoveJusta (Artisan)"

  num <- nrow(subset(boot_data, names == "stoveJusta (HM5000)" & power1 != "."))
  total <- nrow(subset(boot_data, names == "stoveJusta (HM5000)"))
  out$pct[4] <- num*100/total
  out$var[4] <- "stoveJusta (HM5000)"

  num <- nrow(subset(boot_data, names == "stoveRocket Elbow (Chulika)" & power1 != "."))
  total <- nrow(subset(boot_data, names == "stoveRocket Elbow (Chulika)"))
  out$pct[5] <- num*100/total
  out$var[5] <- "stoveRocket Elbow (Chulika)"

  num <- nrow(subset(boot_data, names == "stoveRocket Elbow (G3300)" & power1 != "."))
  total <- nrow(subset(boot_data, names == "stoveRocket Elbow (G3300)"))
  out$pct[6] <- num*100/total
  out$var[6] <- "stoveRocket Elbow (G3300)"

  num <- nrow(subset(boot_data, names == "stoveSunken Pot" & power1 != "."))
  total <- nrow(subset(boot_data, names == "stoveSunken Pot"))
  out$pct[7] <- num*100/total
  out$var[7] <- "stoveSunken Pot"

  num <- nrow(subset(boot_data, names == "stoveThree Stone Fire" & power1 != "."))
  total <- nrow(subset(boot_data, names == "stoveThree Stone Fire"))
  out$pct[8] <- num*100/total
  out$var[8] <- "stoveThree Stone Fire"

  num <- nrow(subset(boot_data, names == "stoveVikram" & power1 != "."))
  total <- nrow(subset(boot_data, names == "stoveVikram"))
  out$pct[9] <- num*100/total
  out$var[9] <- "stoveVikram"

  num <- nrow(subset(boot_data, names == "fuelEucalyptus" & power1 != "."))
  total <- nrow(subset(boot_data, names == "fuelEucalyptus"))
  out$pct[10] <- num*100/total
  out$var[10] <- "fuelEucalyptus"

  num <- subset(boot_data, (names == "fp" | names == "mce" | names == "stoveJusta (Artisan)" |
                              names == "stoveJusta (HM5000)" | names == "stoveRocket Elbow (Chulika)" |
                              names == "stoveRocket Elbow (G3300)" | names == "stoveSunken Pot" |
                              names == "stoveThree Stone Fire" | names == "stoveVikram" |
                              names == "fuelEucalyptus") & power1 != ".")

  # round
  out$pct <- round(out$pct,1)
  var_freq <- out
```

Summary

The table gives the percent of the time each variable appears in any form.

The mfp/bootstrapping method chooses firepower as an important variable more often than mce. 

```{r}
  kable(var_freq)
```

## Overall Conclusions:
Firepower seems to be a meaningful predictor for bc emissions rate. (Although the percent of variance explained is low.)

Firepower is a better predictor than mce for bc emissions rate.

** To Do: Check rmse calculations for boxcox transforms