---
title: "Supporting Information"
output:
  word_document:
    toc: yes
---

```{r load_libraries, echo=FALSE, message=FALSE}
  if (!require("pacman")) install.packages("pacman")
  pacman::p_load(tidyverse, patchwork)
  options(knitr.table.format = "latex")
```

```{r global_options, include=FALSE}
  knitr::opts_chunk$set(fig.path = 'figures/', warning = FALSE,
                        message = FALSE, cache = FALSE)
```

```{r, echo=FALSE}
  lab_temp_fp <- readRDS("../r_files/lab_temp_fp_merged.RDS")
  field_temp <- readRDS("../r_files/india_temp_merged.RDS")
  field_fp <- readRDS("../r_files/field_firepower.RDS")
  field_samples <- readRDS("../r_files/field_samples.RDS")
```

Appendix C1: Scatter plots of change in temperature (above ambient) at the combustion chamber outlet versus log-transferred firepower. Data points are colored by fuel type and spearman’s rho correlation values () are shown for each stove type. The first-order linear regression line of best fit is shown for each stove with a 95% confidence interval. 

```{r, echo=FALSE}
  source("../r_scripts/functions.r")
```

```{r, echo=FALSE}
  lab_temp_log_fp <-
    lab_temp_fp %>%
    dplyr::mutate(log_fp = log(firepower))

  eqns <- by(lab_temp_log_fp, lab_temp_log_fp$stove, rho_temp_fp)

  temp_log_fp_rho <- data.frame(eq = unclass(eqns), stove = names(eqns)) %>%
                     dplyr::filter(!is.na(eq))
```

```{r lab_field_figure_1, fig.height=8, fig.width = 8, echo=FALSE}
  lab_temp_fp %>%
  dplyr::ungroup() %>%
  dplyr::mutate(stove =
                  forcats::fct_relevel(stove,
                                       "Three-stone fire",
                                       "Mud chulha",
                                       "Metal grill",
                                       "Rocket elbow",
                                       "Ceramic plancha",
                                       "Metal plancha",
                                       "Ceramic jiko",
                                       "Metal jiko",
                                       "Forced-draft gasifier"),
                fuel = forcats::fct_relevel(fuel,
                                            "Douglas fir (milled)",
                                            "Eucalyptus (split)",
                                            "Coconut (briquettes)",
                                            "Hardwood (lumps)",
                                            "Eucalyptus (pellets)",
                                            "Red oak (milled)")) %>%
  ggplot(aes(y = log(firepower), x = temp)) +
    geom_point(aes(color = fuel), shape = 1, size = 1, stroke = 0.5) +
    geom_smooth(method = lm, color = "black") +
    scale_color_manual(values = c("#999999", "#E69F00", "yellowgreen", "darkcyan", "coral3", "#0072B2")) +
    guides(colour = guide_legend(override.aes = list(size = 1.5, stroke = 1))) +
    geom_text(data = temp_log_fp_rho, aes(x = Inf, y = -Inf, label = eq,
                                          vjust = -0.75, hjust = 1),
              color = "black",  parse = TRUE, size = 5) +
    theme_minimal() +
    theme(text = element_text(size = 12),
          legend.position = "top",
          legend.title = element_blank()) +
    facet_wrap(.~stove, scales = "free") +
    ylab("Log-Transformed Firepower [log(kW)]") +
    xlab(expression(paste(Delta, " Temperature [", degree, "Celsius]")))
```

Appendix C2: Boxplots of the change in temperature (above ambient) at the combustion chamber outlet and firepower. The boxplots are colored by fuel type and are shown for each stove type.

```{r, echo=FALSE}
  p1 <-
  lab_temp_fp %>%
  dplyr::ungroup() %>%
  dplyr::mutate(stove =
                  forcats::fct_relevel(stove,
                                       "Three-stone fire",
                                       "Mud chulha",
                                       "Metal grill",
                                       "Rocket elbow",
                                       "Ceramic plancha",
                                       "Metal plancha",
                                       "Ceramic jiko",
                                       "Metal jiko",
                                       "Forced-draft gasifier"),
                fuel = forcats::fct_relevel(fuel,
                                            "Douglas fir (milled)",
                                            "Eucalyptus (split)",
                                            "Coconut (briquettes)",
                                            "Hardwood (lumps)",
                                            "Eucalyptus (pellets)",
                                            "Red oak (milled)")) %>%
  ggplot(aes(y = firepower, x = stove)) +
    geom_boxplot(aes(color = fuel)) +
    scale_color_manual(values = c("#999999", "#E69F00", "yellowgreen", "darkcyan", "coral3", "#0072B2")) +
    theme_minimal() +
    theme(text = element_text(size = 12),
          axis.text.x = element_text(angle = 25, vjust = 1, hjust = 1),
          legend.position = "top",
          axis.title.x = element_blank(),
          legend.title = element_blank()) +
    ylab("Firepower [kW]") +
    xlab("")
```

```{r, echo=FALSE}
  p2 <-
  lab_temp_fp %>%
  dplyr::ungroup() %>%
  dplyr::mutate(stove =
                  forcats::fct_relevel(stove,
                                       "Three-stone fire",
                                       "Mud chulha",
                                       "Metal grill",
                                       "Rocket elbow",
                                       "Ceramic plancha",
                                       "Metal plancha",
                                       "Ceramic jiko",
                                       "Metal jiko",
                                       "Forced-draft gasifier"),
                fuel = forcats::fct_relevel(fuel,
                                            "Douglas fir (milled)",
                                            "Eucalyptus (split)",
                                            "Coconut (briquettes)",
                                            "Hardwood (lumps)",
                                            "Eucalyptus (pellets)",
                                            "Red oak (milled)")) %>%
  ggplot(aes(y = temp, x = stove)) +
    geom_boxplot(aes(color = fuel)) +
    scale_color_manual(values = c("#999999", "#E69F00", "yellowgreen", "darkcyan", "coral3", "#0072B2")) +
    theme_minimal() +
    theme(text = element_text(size = 12),
          axis.text.x = element_text(angle = 25, vjust = 1, hjust = 1),
          legend.position = "none",
          legend.title = element_blank()) +
    ylab(expression(paste(Delta, " Temperature [", degree, "Celsius]"))) +
    xlab("")
```

```{r, fig.height=6, fig.width=8, echo=FALSE}
  p1 + p2 + plot_layout(nrow = 2)
```

