---
title: "lab gravimetric data"
output:
  html_document:
    toc: true
    toc_float: true
    theme: paper
---

```{r global_options, include=FALSE}
  knitr::opts_chunk$set(fig.path='figures/', warning=FALSE, message=FALSE, cache=FALSE)
```

```{r load_libraries}
  library(tidyverse)
  library(forcats)
  library(gridExtra)
```

# Load files

* data

```{r load_data}
  grav <- readRDS("../r_files/lab_grav.RDS")
```

* functions

```{r load_functions}
  source("../r_scripts/plots.R")
  source("../r_scripts/functions.R")
```

* metadata

```{r load_meta}
  samples <- readRDS("../r_files/lab_meta.RDS")
```

# Organize data

* tidy data

```{r tidy_data}
  grav <- grav %>%
          dplyr::mutate(dur = (end_time - start_time) * (86400 / 60)) %>%
          dplyr::mutate(sample_id = gsub("Start Up|Start up", "start_up", sample_id),
                        sample_id = gsub("Shut Down", "shutdown", sample_id),
                        sample_id = gsub(" [:(:][0-9])|^2nd |/Restart", "", sample_id),
                        sample_id = gsub("Sample 2|Sample 2 [:(:]2nd try[:):]", "fp_1", sample_id),
                        sample_id = gsub("Sample 3", "fp_2", sample_id),
                        sample_id = gsub("Sample 4|Relight|Restart", "fp_3", sample_id),
                        sample_id = gsub("Sample 5|Sample5", "fp_4", sample_id),
                        sample_id = gsub("Sample 6", "fp_5", sample_id),
                        sample_id = gsub("Sample 7", "fp_6", sample_id),
                        sample_id = gsub("Sample 8", "fp_7", sample_id),
                        sample_id = factor(sample_id,
                                           levels = c("start_up", "fp_1", "fp_2", "fp_3",
                                                      "fp_4", "fp_5", "fp_6", "fp_7", "shutdown"))) 

  # fix typos
  fp4 <- c(156, 184, 198, 226, 240, 247, 268, 275)
  fp5 <- c(157, 185, 199, 227, 241, 248, 269, 276)
  grav$sample_id[fp4] <- "fp_4" 
  grav$sample_id[fp5] <- "fp_5"
```

```{r extract_times}
  filter_times <- grav %>% 
                  dplyr::select(id, date, sample_id, start_time, end_time, dur)
```


* add stove fuel information 

```{r add_test_info}
  grav <- grav %>%
          dplyr::left_join(samples, by = "id")
```

# Arrange data

* select variables
* convert to long format
* add units

```{r}
  grav_merged <- grav %>% 
                 dplyr::select(id, date, sample_id, pm_mass, pm_ef, pm_rate,
                               bc_mass, bc_ef, bc_rate, fp, mce) %>%
                 tidyr::gather("var", "val", 4:11) %>%
                 dplyr::mutate(units = ifelse(grepl("mass", var), "miligrams",
                                              "grams per kilogram of fuel"),
                               units = ifelse(grepl("rate", var), "miligrams per minute",
                                              units),
                               units = ifelse(var == "fp", "kilowatts", units),
                               units = ifelse(var == "mce", '', units)) %>%
                 dplyr::mutate(qc = factor("ok", c("bad", "maybe", "ok")))
```

## Plot: Time series of burns

Pollutant metrics:

* grouped by pollutant type
* plotted in time
* color shows qc

```{r, echo=FALSE}
  grav_merged %>%
    ggplot(aes(x = date, y = val, color = qc)) +
    geom_point() +
    theme_bw() +
    facet_wrap(~var, scales = "free")
```

Conclusion: No obvious trends in time.

## Plot: Metrics by stove type

* plotted by stove type
* colored by fuel type
* samples are background corrected

```{r, echo=FALSE, fig.height = 16, fig.width = 16}
  pah_samples_p <-
    pah_samples_sum %>%
    dplyr::filter(!is.na(conc), !grepl("27|28|29|30", id)) %>%
    dplyr::left_join(dplyr::select(samples, id, stove, fuel, stovecat, fuelcat), by = "id") %>%
    dplyr::mutate(stove = 
                    stove %>% 
                    tolower %>%
                    gsub(" [:(:].*[:):]", "", .) %>%
                    forcats::fct_relevel("three stone fire",
                                         "clay ring",
                                         "ceramic charcoal",
                                         "rocket elbow",
                                         "built-in justa",
                                         "metal charcoal",
                                         "fan rocket elbow",
                                         "gasifier",
                                         "wick kerosene",
                                         "pressure kerosene",
                                         "lpg"),
                  fuel = 
                    fuel %>% 
                    tolower,
                  stovecat = 
                    stovecat %>%
                    forcats::fct_recode("insulated [improved] stoves" = "improved",
                                        "insulated [improved] stoves" = "gasifiers",
                                        "liquid-fuel stoves" = "advanced",
                                        "traditional stoves" = "traditional"),
                  fuelcat =
                    fuelcat %>%
                    forcats::fct_recode("liquid" = "advanced"))
  pah_samples_p %>%
    ggplot(aes_string(x = "stove", y = "conc")) +
      geom_boxplot(outlier.colour = NA) +
      geom_jitter(aes(color = factor(fuel)), size = 4,  width = 0.2, shape = 1, stroke = 2) + 
      scale_shape(solid = FALSE) +
      guides(fill = FALSE) +
      theme_bw() +
      theme(text = element_text(size = 20),
            axis.text.x = element_text(angle = 15, hjust = 1, vjust = 1),
            legend.position = "top") +
      facet_wrap(pol~stovecat, ncol = 3, scales = "free") +
      labs(color = "fuel type") +
      ylab("") +
      xlab("")
```

Conclusion: Some of our liquid fuel stoves have NA values for pollutants of interest, would rerunning these samples at higher concentrations allow us to resolve values for these stoves?

## Table: Outliers by stove type

When tests are grouped by pollutant and stove type the following have z-scores greater than three:

```{r, echo=FALSE}
  pah_samples_p %>%
    dplyr::filter(!is.na(conc)) %>%
    dplyr::group_by(pol, stove) %>%
    dplyr::mutate(z_score = (conc - mean(conc, na.rm = TRUE))/ sd(conc, na.rm = TRUE)) %>%
    dplyr::ungroup() %>%
    dplyr::select(id, pol, stove, fuel, z_score) %>%
    dplyr::filter(z_score > 3) %>%
    dplyr::rename("pah type" = "pol") %>%
    knitr::kable("markdown", align = 'c')
```

# Save data

```{r}
  saveRDS(grav_merged, "../r_files/lab_grav_merged.RDS")
```

```{r}
  # write_csv(grav_merged %>%
  #             dplyr::left_join(filter_times, by = c("id", "sample_id")) %>%
  #             dplyr::filter(var == "pm_ef") %>%
  #             tidyr::spread(var, val), "../r_csv/lab_grav.csv")
```

