---
title: "Lab to field model"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
---

```{r global_options, include=FALSE}
  knitr::opts_chunk$set(fig.path='figures/', warning=FALSE, message=FALSE, cache=FALSE)
```

```{r load_libraries, echo=FALSE}
  library(tidyverse)
```

# Load files

* data

```{r load_data, echo=FALSE}
  lab_grav <- readRDS("../r_files/lab_grav_merged.RDS")
  field_emissions <- readRDS("../r_files/field_emissions.RDS")
```

* functions

```{r load_functions, echo=FALSE}
  source("../r_scripts/models.R")
  source("../r_scripts/functions.R")
```

* metadata

```{r load_meta, echo=FALSE}
  lab_samples <- readRDS("../r_files/lab_meta.RDS")
  field_samples <- readRDS("../r_files/field_meta.RDS")
```

# Tidy data

## Lab data

* remove start up and shutdown
* select only wood tests
* filter out Okote tests
* create general stove categories

```{r, echo=FALSE}
  lab_data <- lab_grav %>%
              dplyr::select(-units) %>%
              tidyr::spread(var, val) %>% 
              dplyr::select(id, sample_id, pm_ef, bc_ef, pm_mass, bc_mass,
                            pm_rate, bc_rate, fp, mce) %>%
              tidyr::gather("pol", "val", 3:8) %>%
              dplyr::left_join(lab_samples, by = "id") %>%
              dplyr::filter(sample_id != "start_up", sample_id != "shutdown") %>% 
              dplyr::filter(fuel != "Okote") %>%
              dplyr::filter(!grepl("mass", pol)) %>%
              dplyr::filter(fuel_type == "wood") %>%
              dplyr::filter(!is.na(val), !is.na(fp), !is.na(mce)) %>%
              dplyr::mutate(stove_cat = "traditional open fire",
                            stove_cat = ifelse(grepl("Rocket", stove),
                                               "rocket elbow", stove_cat),
                            stove_cat = ifelse(grepl("Sunken|Justa", stove),
                                               "built-in", stove_cat))
```

## Field data

* create general stove categories

```{r, echo=FALSE}
  field_data <- field_emissions %>%
                dplyr::filter(grepl("pm|bc|firepower|mce", var)) %>%
                dplyr::select(-units, - pol) %>%
                tidyr::spread(var, val) %>%
                dplyr::select(hh_id, pm_ef, bc_ef, pm_mass, bc_mass,
                              pm_rate, bc_rate, firepower, mce) %>%
                dplyr::rename(fp = firepower) %>%
                tidyr::gather("pol", "val", 2:7) %>%
                dplyr::filter(!grepl("mass", pol)) %>%
                dplyr::left_join(dplyr::select(field_samples, hh_id,
                                               stove_type, fuel_type), by = "hh_id") %>%
                dplyr::filter(!is.na(val), !is.na(fp), !is.na(mce)) %>%
                dplyr::mutate(stove_cat = "traditional open fire",
                              stove_cat = ifelse(grepl("Rocket", stove_type),
                                                 "rocket elbow", stove_cat))
```

# Develop models using lab data

## Firepower models (with diagnostics)

* define basic model

```{r}
  f <- c("val ~ fp")
```

A unique model is created for each stove category and each pollutant type. Each model has five diagnostic plots:

* regression plot colored by firepower sample id which displays the fitted linear model and confidence interval [95%]
* residual vs. fitted plot to show whether residuals have non-linear patterns.
* normal q-q plot to show whether the residuals are normally distributed. 
* scale-location plot to check that the residuals are spread equally along the range of predictors (homoscedasticity)
* residuals vs. leverage plot to check for influential cases (outliers)

```{r, fig.height=6, fig.width=6, echo=FALSE, results='hide', fig.keep='all'}
  lapply(f, function(x) plot_simple_lm(data = lab_data, eqn = x))
```

## Firepower model summary table

```{r make_fp_table, echo=FALSE}
  fp_models <- lapply(f, function(x) table_simple_lm(data = lab_data, eqn = x)) %>%
               dplyr::bind_rows() %>%
               dplyr::arrange(desc(r2)) %>%
               dplyr::mutate(equation = f)
```

```{r, echo=FALSE}
  knitr::kable(fp_models, align = 'c')
```

## Firepower model conclusions
* Best linear fits: black carbon rate, 

## MCE models (with diagnostics)

* basic model

```{r}
  f <- c("val ~ mce")
```

A unique model is created for each stove category and each pollutant type. Each model has five diagnostic plots:

* regression plot colored by firepower sample id which displays the fitted linear model and confidence interval [95%]
* residual vs. fitted plot to show whether residuals have non-linear patterns.
* normal q-q plot to show whether the residuals are normally distributed. 
* scale-location plot to check that the residuals are spread equally along the range of predictors (homoscedasticity)
* residuals vs. leverage plot to check for influential cases (outliers)

```{r, fig.height=6, fig.width=6, echo=FALSE, results='hide', fig.keep='all'}
  lapply(f, function(x) plot_simple_lm(data = lab_data, eqn = x))
```

## MCE model summary table

```{r make_mce_table, echo=FALSE}
  mce_models <- lapply(f, function(x) table_simple_lm(data = lab_data, eqn = x)) %>%
                dplyr::bind_rows() %>%
                dplyr::arrange(desc(r2)) %>%
                dplyr::mutate(equation = f)
```

```{r, echo=FALSE}
  knitr::kable(mce_models, align = 'c')
```

# Predict field data using lab data

## Test firepower only models

```{r}
  predict_field <- dplyr::left_join(field_data, fp_models, by = c("stove_cat", "pol")) %>%
                   dplyr::mutate(pred_val = fp*slope + intercept)
```

```{r, echo=FALSE, fig.height=15, fig.width=15}
  plot_test_models(predict_field)
```

## Test mce only models

```{r}
  predict_field <- dplyr::left_join(field_data, mce_models, by = c("stove_cat", "pol")) %>%
                   dplyr::mutate(pred_val = mce*slope + intercept)
```

```{r, echo=FALSE, fig.height=15, fig.width=15}
  plot_test_models(predict_field)
```
