---
title: "Load and save data"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
---

```{r library, echo=FALSE}
  library(tidyverse)
  library(knitr)
```

```{r global_options, include=FALSE}
  knitr::opts_chunk$set(fig.path='figures/', warning=FALSE, message=FALSE, cache=FALSE)
```

```{r functions, echo=FALSE}
  source("../r_scripts/load_data.R")
  source("../r_scripts/load_metadata.R")
```

# Field instrument data (raw)

* Load and save thermocouple data

```{r field_temp} 
  # this function gives warnings due to slightly varied file formats 
  # however the output is correct
  saveRDS(load_field_temp(), file = "../r_files/field_temp.RDS")
```

* Load and save sums data

```{r field_sums} 
  saveRDS(load_field_sums(), file = "../r_files/field_sums.RDS")
```

* Load and save gravimetric data

```{r field_grav} 
  saveRDS(load_field_grav(), file = "../r_files/field_grav.RDS")
```

* Load and save air quality expert data

```{r field_aqe} 
  # this function gives warnings due to slightly varied file formats 
  # however the output is correct
  saveRDS(load_field_aqe(), file = "../r_files/field_aqe.RDS")
```
 
## Field data logs

* Load sampling times and household info

```{r field_metadata} 
  saveRDS(load_field_meta(), file = "../r_files/field_meta.RDS")
```

* Load and save flow rate data

```{r field_flows} 
  saveRDS(load_field_flows(), file = "../r_files/field_flows.RDS")
```

* Load and save filter metadata

```{r field_filter_meta} 
  saveRDS(load_field_filter_meta(), file = "../r_files/field_filter_meta.RDS")
```

* Load and save temperature metadata

```{r field_temp_meta} 
  saveRDS(load_field_temp_meta(), file = "../r_files/field_temp_meta.RDS")
```

* Load and save testing notes

```{r field_notes} 
  saveRDS(load_field_notes(), file = "../r_files/field_notes.RDS")
```

* Load and save testing events

```{r field_events} 
  saveRDS(load_field_events, file = "../r_files/field_events.RDS")
```

# Lab data (cleaned)
